### 2022-11-09 Manuscripts/main.tex
Update markdown

\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{calrsfs}
\usepackage{pgfplots}
\usepackage[affil-it]{authblk}
\usepackage{color}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{manyfoot}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{soul}
\usepackage[charter,cal=cmcal]{mathdesign} % Specify font for serif family
\usepackage{avant} % Specify avant font for sans serif family
\usepackage{mathtools} % Replaces amsmath
\usepackage{sectsty} % Specify section formatting
	\sectionfont{\sffamily\color{DarkBlue}}
	\subsectionfont{\sffamily\color{LightBlue}}
	\subsubsectionfont{\small\sffamily}

\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
\newcommand{\La}{\mathcal{L}}
\newcommand{\Lb}{\pazocal{L}}
\newcommand{\la}{\mathcal{l}}
\newcommand{\lb}{\pazocal{l}}
\newcommand{\M}{\pazocal{M}}
\newcommand{\Ha}{\mathcal{H}}
\newcommand{\Hb}{\pazocal{H}}
\newcommand{\Pa}{\mathcal{P}}
\newcommand{\Pb}{\pazocal{P}}

% Reference
\definecolor{wine_red}{RGB}{178, 8, 56}
% Emphasizing term
\definecolor{lan_red}{RGB}{238, 46, 36}
\definecolor{ReD}{RGB}{255,0,0}
% Emphasizing number
\definecolor{violet}{RGB}{133, 12, 112}
% Comments and footnotes
\definecolor{sea_blue}{RGB}{0, 84, 158}
% Axlers
\definecolor{axler_yellow}{RGB}{255, 250, 198}
\definecolor{background}{RGB}{251, 252, 240}
\definecolor{light_blue}{RGB}{235, 240, 252}

\hypersetup{
    colorlinks = true,
    linkcolor = wine_red
}

\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}
\newcommand{\Q}{\mathbb Q}
\newcommand{\F}{\mathbb F}
\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\imply}[0]{\Rightarrow}
\newcommand{\emphasize}[1]{\textcolor{ReD}{\textbf{\hl{#1}}}}
\newcommand{\important}[1]{{\textbf{\hl{#1}}}}
\newcommand{\num}[1]{\textcolor{violet}{\emph{\textbf{#1}}}}
\newcommand{\foot}[1]{{\footnote{\textcolor{sea_blue}{#1}}}}
\newcommand{\leftb}{\left(}
\newcommand{\rightb}{\right)}
\newcommand{\inner}[2]{$\langle${$#1$},{$#2$}$\rangle$}
\newcommand{\innereq}[2]{\langle{#1},{#2}\rangle}
\newcommand{\innerproduct}[1]{$\langle${$#1$}$\rangle$}
\newcommand{\innerproducteq}[1]{\langle{#1}\rangle}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\abs}[1]{|#1|}
\newcommand{\braket}[1]{\left\{ {#1} \right\}}
\newcommand{\qedwhite}{\hfill \ensuremath{\Box}}
\newcommand{\compart}{{\color{lan_red}\rule{\linewidth}{0.5mm}}} 
\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\vect}[1]{\left( #1 \right)}

\newcommand{\dimension}{\text{dim}}
\newcommand{\nullspace}{\text{null}}
\newcommand{\range}{\text{range}}
\newcommand{\operator}[1]{#1 \in \Lb(V)}
\newcommand{\operatorspace}[2]{#1 \in \Lb(#2)}
\newcommand{\V}{\R^n}

\pagestyle{fancy}
\fancyhead[L]{Blair Yang}
\fancyhead[R]{Supplementary Materials}

\usepackage{xcolor} % required to defined colours
	\definecolor{DarkBlue}{HTML}{25355A}
	\definecolor{LightBlue}{HTML}{007FA3}
	\definecolor{Yellow}{HTML}{A37500}
	\definecolor{Red}{HTML}{A3002E}
	\definecolor{Skyblue}{HTML}{007FA3}
	\definecolor{Background_red}{HTML}{F6E5EA}
	\definecolor{bgyellow}{HTML}{F2ECD9}
	\definecolor{darkyellow}{HTML}{A07300}
	\definecolor{lan_purple}{HTML}{850C70}

% \usepackage[sfdefault]{carlito}
% \usepackage{fontspec}
% \setmainfont{Arial}

\newcommand{\urlref}{\hl{[REF]}}
\newcommand{\pendingref}{\textbf{\hl{[REF]}}$ \ $}
\newcommand{\unknownref}{\textcolor{ReD}{\textbf{\hl{[REF]}}}$ \ $}
\newcommand{\pendingdata}{\textbf{\hl{$<$DATA$>$}}$ \ $}
\newcommand{\unknowndata}{\textcolor{ReD}{\textbf{\hl{$<$DATA$>$}}}$ \ $}

\title{Supplementary Materials}
\author{Blair Yang}
\date{August 2022}

\begin{document}

\section*{Style}
\urlref $ \ \ \ $Pending reference, with the following URL\\
\pendingref $ \ \ $ Pending reference, with the following URL\\
\unknownref $ \ \ $ Pending reference, with un-specified topic (need to find relevant papers)\\
\pendingdata $ \ \ $ Pending data, need to be filled with data from the cited papers\\
\unknowndata $ \ \ $ Pending data, need to be find relevant paper with such data

\section{Methodology (supplementary material)}
\subsection{Data acquisition}

\subsubsection{Epidemiological data}

We acquired the time-series data of COVID-19 cases, deaths, and vaccination data in the 26 Public health units (PHU) since January 2020 from Ontario public health. \cite{ref1} The original data was stratified into \pendingdata age bands (\pendingdata).

\subsubsection{Vaccine data}

We acquired the provincial time-series vaccination data in Ontario from Ontario public health, covering the percentage population who has taken first does, second dose, and third does. We assumed a uniform distribution of the vaccination population ratio for every PHU.

\subsubsection{Labour force data}

We used the labour force age distribution of Canada from \pendingref \emphasize{(2016 Census)} in year \pendingdata and the employment rate in August 2022 \pendingdata by statistics Canada \pendingref.

\subsubsection{Commute data}

The commuting data in Ontario was excerpted from the 2016 demographic census. We assumed a constant age distribution.

\subsection{Data Calibration}

\subsubsection{Age-specific data calibration}

Due to the different dimensionality of the contact matrix in Canada (16 age-bands with 5-years sensitivity) and the Ontario epidemiological data (6 age-bands with 10-years sensitivity), we augmentation all of the age-specific data using difference of Gaussians (DoG), the estimated percentage population with certain characteristic (i.e, cases, deaths, vaccinated) with an integer-valued age $i$ is estimated to be:
\begin{gather}
    \mu_{i} = \Gamma_{\sigma_1, \sigma} (i) = \frac{e^{-\frac{i^2}{2 \sigma_1^2}}}{\sigma_1 \sqrt{2\pi}} I - \frac{e^{-\frac{i^2}{2 \sigma_2^2}}}{\sigma_2 \sqrt{2\pi}} I = \sum_{\mu \in I} \frac{e^{-\frac{(i - \mu_1)^2}{2 \sigma_1^2}}}{\sigma_1 \sqrt{2\pi}} \mu_2 - \frac{e^{-\frac{(i - \mu_1)^2}{2 \sigma_2^2}}}{\sigma_2 \sqrt{2\pi}} \mu_2
\end{gather}
Where $i$ is a positive integer which denotes to the age of distribution, I denotes to the set of the raw age distribution with a 10-years age sensitivity, $\sigma_1, \sigma_2$ denotes to two positive constants, $\mu = \vect   {\mu_1, \mu_2}$ is a tuple with the median age of the age band and percentage distribution at 1st and 2nd entry, respectively. We then integrated the age of each six age bands.

\subsubsection{Prevalence calibration}

\hl{Source} suggested that there are significant underascertainment of the number of cases and deaths of COVID-19 in Canada. \cite{ref2} \cite{ref3} We calculated the average of the underascertainment ratio of \pendingdata and assumed the number to be constant throughout the pandemic.

\subsubsection{Vaccine immunity level estimation}

\hl{Source} suggested that the waning effect of COVID-19 vaccine efficacy.

\bibliographystyle{plain}

\begin{thebibliography}{99}
\bibitem{ref1}{Public Health Ontario. Ontario COVID-19 Data Tool. Datasets - ontario data catalogue. Retrieved August 21, 2022, from https://data.ontario.ca/en/dataset?groups=2019-novel-coronavirus}

\bibitem{ref2}{Bolotin, S., Tran, V., Deeks, S. L., Peci, A., Brown, K. A., Buchan, S. A., Ogbulafor, K., Ramoutar, T., Nguyen, M., Thakkar, R., DelaCruz, R., Mustfa, R., Maregmen, J., Woods, O., Krasna, T., Cronin, K., Osman, S., Joh, E., $\&$amp; Allen, V. G. (2021). Assessment of population infection with SARS-COV-2 in Ontario, Canada, March to June 2020. Eurosurveillance, 26(50). https://doi.org/10.2807/1560-7917.es.2021.26.50.2001559}

\bibitem{ref3}{Anand, S. S., Arnold, C., Bangdiwala, S. I., Bolotin, S., Bowdish, D., Chanchlani, R., de Souza, R. J., Desai, D., Kandasamy, S., Khan, F., Khan, Z., Langlois, M.-A., Limbachia, J., Lear, S. A., Loeb, M., Loh, L., Manoharan, B., Nakka, K., Pelchat, M., … Wahi, G. (2022). Seropositivity and risk factors for SARS-COV-2 infection in a South Asian community in Ontario: A cross-sectional analysis of a prospective cohort study. CMAJ Open, 10(3). https://doi.org/10.9778/cmajo.20220031 }
\end{thebibliography}

\end{document}

### 2022-11-09 Model/Dependency.py
distributing cases to counties

@@ -16,13 +16,26 @@ class Dependency:
     matrix_by_class = [[None] * 4, [None] * 4]
 
     code_to_name = dict()
-    code_to_phu = dict()
-    phu_to_code = dict()
+    district_to_phu = dict()
+    phu_to_district = dict()
     code_to_index = dict()
+    county_to_district = dict()
+    district_to_county = dict()
 
     band_to_population = dict()
-    date_to_cases_by_phu = dict()
+    date_to_incidence_rate_by_phu = dict()
+    date_to_hospitalization_rate_by_phu = dict()
+    date_to_death_rate_by_phu = dict()
     date_to_vaccines_by_age = np.zeros((0, 3, 9))
+
+
+    date_to_no_cases_by_county = dict()
+    date_to_no_cases_by_county = dict()
+    date_to_no_cases_by_county = dict()
+    date_to_no_cases_by_county = dict()
+
+    population_by_phu = dict()
+    population_by_district = dict()
 
     def __init__(self):
         self.read_files()
@@ -43,13 +56,12 @@ class Dependency:
         self.read_cases()
         self.read_vaccine()
         self.reshape_vaccine()
-        self.differentiate()
-        print(self.date_to_cases_by_phu)
-        for i in range(len(self.date_to_cases_by_phu.keys())):
-            print(i)
-            # print(list(self.date_to_cases_by_phu.keys()))
-            # print(list(self.date_to_cases_by_phu.keys())[i])
-            # print(list(self.phu_to_code.keys())[i])
+        """
+            Do not differentiate cases
+        """
+        # self.differentiate()
+        self.code_district_linking()
+        self.compute_phu_population()
 
     def read_matrix(self):
         """
@@ -79,7 +91,7 @@ class Dependency:
             county_data: 520 * 3 float-valued np.array
             county_data[0:520][0] is the county code
             county_data[0:520][1] is the district code
-            county_data[0:520][2] is the population code
+            county_data[0:520][2] is the population
         """
         read_path = self.get_dependency_path() + 'Ontario_county_data.csv'
         with open(read_path) as file:
@@ -89,7 +101,7 @@ class Dependency:
             elements = lines[line].split(',')
             self.county_data[line - 1] = [elements[0], elements[5], elements[4]]
             self.code_to_name[elements[0]] = elements[1]
-            self.county_codes.append(elements[0])
+            self.county_codes.append(int(elements[0]))
[…]

### 2022-11-09 Model/ModelData.py

@@ -50,5 +50,5 @@ class ModelData:
         self._time_series_deaths = np.zeros(shape=(x, y, z), dtype=int)
 
 
-
-
+if __name__ == '__main__':
+    pass

### 2022-11-09 Model/TestDependency.py

@@ -1,0 +1,11 @@
+import math
+import numpy as np
+import Dependency as Dependency
+from ModelData import ModelData
+import Parameters
+
+
+d = Dependency.Dependency()
+# print(d.commute_matrix.shape)
+# print(d.date_to_cases_by_phu.keys())
+print(d.date_to_vaccines_by_age.shape)

### 2022-11-09 Model/test.py

@@ -49,7 +49,13 @@ test = np.random.randint(20, size=(100, 16))
 ratio = np.ones(shape=(16, 1), dtype=float)
 
 raw_kernel = Parameters.EXP2ACT_CONVOLUTION_KERNEL
-kernel = np.matmul(ratio, np.transpose(raw_kernel.reshape((raw_kernel.shape[0], 1))))
+transposed = np.transpose(raw_kernel.reshape((raw_kernel.shape[0], 1)))
+
+print(raw_kernel, raw_kernel.shape)
+print(transposed, transposed.shape)
+print(ratio, ratio.shape)
+
+kernel = np.matmul(ratio, transposed)
 kernel_size = kernel.shape[0]
 
 data = np.flip(test[date - kernel_size:date], axis=0)

### 2022-11-10 Model/Dependency.py
做完了！

@@ -1,6 +1,7 @@
 from datetime import datetime
 import numpy as np
 import os
+import csv
 
 import Gaussian
 import Parameters
@@ -28,11 +29,9 @@ class Dependency:
     date_to_death_rate_by_phu = dict()
     date_to_vaccines_by_age = np.zeros((0, 3, 9))
 
-
-    date_to_no_cases_by_county = dict()
-    date_to_no_cases_by_county = dict()
-    date_to_no_cases_by_county = dict()
-    date_to_no_cases_by_county = dict()
+    date_to_cases_by_county = None
+    date_to_hospitalizations_by_county = None
+    date_to_deaths_by_county = None
 
     population_by_phu = dict()
     population_by_district = dict()
@@ -62,6 +61,7 @@ class Dependency:
         # self.differentiate()
         self.code_district_linking()
         self.compute_phu_population()
+        self.distribute_to_counties()
 
     def read_matrix(self):
         """
@@ -113,6 +113,7 @@ class Dependency:
         lines = contents.split('\n')
         for line in range(1, len(lines) - 1):
             elements = [lines[line][:lines[line].index(',')], lines[line][lines[line].index(',') + 1:]]
+            elements[1] = elements[1].replace('"', '')
             self.district_to_phu[int(elements[0])] = elements[1]
             if elements[1] not in self.phu_to_district:
                 self.phu_to_district[elements[1]] = [int(elements[0])]
@@ -152,18 +153,24 @@ class Dependency:
            :return:
         """
         read_path = self.get_dependency_path() + 'All case trends data.csv'
-        with open(read_path) as file:
-            contents = file.read()
-        lines = contents.split('\n')
+        with open(read_path, newline='') as file:
+            reader = csv.reader(file, delimiter=',')
+            lines = list(reader)
 
         self.find_max_date()
 
+        last_recorded = 0
+
         for line in range(1, len(lines) - 1):
-            elements = lines[line].split(',')
+            elements = lines[line]
+            # print(elements)
+            elements[1] = elements[1].replace('"', '')
             string = elements[0]
             this_day = datetime.strptime(string, '%d-%b-%y')
             after_outbreak = (this_day - Parameters.OUTBREAK_FIRST_DAY).days
             phu = elements[1]
+            if after_outbreak > last_recorded:
+                last_recorded = after_outbreak
             if phu == 'Ontario':
                 pass
             else:
[…]

### 2022-11-10 Model/ModelData.py

@@ -20,22 +20,24 @@ class ModelData:
     _time_series_ICU = None
     _time_series_recovered = None
     _time_series_deaths = None
-
     _time_series_immunized = None
+
+    _time_series_immunity = None
 
     def __init__(self, forecast_days=1000, dependency=None):
         """
             Initialize the tensors
             shape=(x, y, z)
             Here, it should be (x * 528 * 16)
-             x = number of days to forecast + dates elapsed since Covid outbreak
-            y = number of counties
+            x = number of counties
+            y = number of days to forecast + dates elapsed since Covid outbreak
             z = 16 age bands
         """
         self.dependency = dependency
         self._time_series_len = self.dependency.total_days + forecast_days
-        x = self._time_series_len
-        y = len(self.dependency.county_data)
+
+        x = len(self.dependency.county_data)
+        y = self._time_series_len
         z = 16
 
         # print(self._time_series_len)
@@ -48,6 +50,9 @@ class ModelData:
         self._time_series_ICU = np.zeros(shape=(x, y, z), dtype=int)
         self._time_series_recovered = np.zeros(shape=(x, y, z), dtype=int)
         self._time_series_deaths = np.zeros(shape=(x, y, z), dtype=int)
+        self._time_series_immunized = np.zeros(shape=(x, y, z), dtype=int)
+
+        self._time_series_immunity = np.zeros(shape=(x, y, z), dtype=float)
 
 
 if __name__ == '__main__':

### 2022-11-10 Model/Parameters.py

@@ -35,6 +35,16 @@ NO_DISTRICT = 49
 OUTBREAK_FIRST_DAY = datetime.datetime(2020, 1, 15)
 
 """
+    Ontario age-specific parameters, need to update
+"""
+
+# TODO: Do some research and update the following parameters
+
+ONT_CASE_DISTRIBUTION = np.ones(shape=(16, ), dtype=float) / 16
+ONT_HOSP_DISTRIBUTION = np.ones(shape=(16, ), dtype=float) / 16
+ONT_DEATH_DISTRIBUTION = np.ones(shape=(16, ), dtype=float) / 16
+
+"""
     Age-specific parameters, all 16 entries long
 """
 

### 2022-11-10 Model/Dependency.py
做完了！

@@ -363,16 +363,16 @@ class Dependency:
 
             incidences = self.date_to_incidence_rate_by_phu[phu].reshape(self.total_days, 1)
             cases_ratio = Parameters.ONT_CASE_DISTRIBUTION.reshape(16, 1)
-            self.date_to_cases_by_county[i] = np.matmul(incidences, cases_ratio.T) * population / 10000.0
+            self.date_to_cases_by_county[i] = np.matmul(incidences, cases_ratio.T) * population / 100000.0
 
             hospitalizations = self.date_to_hospitalization_rate_by_phu[phu].reshape(self.total_days, 1)
             hospitalization_ratio = Parameters.ONT_HOSP_DISTRIBUTION.reshape(16, 1)
             self.date_to_hospitalizations_by_county[i] = np.matmul(hospitalizations, hospitalization_ratio.T) * \
-                                                         population / 10000.0
+                                                         population / 100000.0
 
             deaths = self.date_to_death_rate_by_phu[phu].reshape(self.total_days, 1)
             deaths_ratio = Parameters.ONT_DEATH_DISTRIBUTION.reshape(16, 1)
-            self.date_to_deaths_by_county[i] = np.matmul(deaths, deaths_ratio.T) * population / 10000.0
+            self.date_to_deaths_by_county[i] = np.matmul(deaths, deaths_ratio.T) * population / 100000.0
 
 
 if __name__ == '__main__':

### 2022-11-10 Model/Parameters.py

@@ -38,11 +38,20 @@ OUTBREAK_FIRST_DAY = datetime.datetime(2020, 1, 15)
     Ontario age-specific parameters, need to update
 """
 
-# TODO: Do some research and update the following parameters
+# TODO: Do some research and update the following parameters, IT IS INCORRECT!!!!!!!
 
-ONT_CASE_DISTRIBUTION = np.ones(shape=(16, ), dtype=float) / 16
-ONT_HOSP_DISTRIBUTION = np.ones(shape=(16, ), dtype=float) / 16
-ONT_DEATH_DISTRIBUTION = np.ones(shape=(16, ), dtype=float) / 16
+ONT_CASE_DISTRIBUTION = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 0.106146399, 0.106351741,
+                                0.105920522, 0.103210008, 0.098220198, 0.10624907, 0.098138062, 0.065560558,
+                                0.042213176, 0.025934691, 0.016273351])
+
+ONT_HOSP_DISTRIBUTION = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 0.106146399, 0.106351741,
+                                0.105920522, 0.103210008, 0.098220198, 0.10624907, 0.098138062, 0.065560558,
+                                0.042213176, 0.025934691, 0.016273351])
+
+ONT_DEATH_DISTRIBUTION = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 0.106146399, 0.106351741,
+                                0.105920522, 0.103210008, 0.098220198, 0.10624907, 0.098138062, 0.065560558,
+                                0.042213176, 0.025934691, 0.016273351])
+
 
 """
     Age-specific parameters, all 16 entries long

### 2022-11-10 Model/testnumpy.py

@@ -1,0 +1,11 @@
+import numpy as np
+
+ratio = np.random.rand(16,)
+ratio = np.ones(shape=(16))
+data = np.random.rand(925)
+
+raito = np.transpose(ratio)
+
+rslt = np.matmul(data, raito)
+
+print(rslt.shape)

### 2022-11-10 Model/Dependency.py
It can run now.

@@ -377,6 +377,4 @@ class Dependency:
 
 if __name__ == '__main__':
     dependency = Dependency()
-    # dependency.read_files()
-    # dependency.compute_phu_population()
     pass

### 2022-11-10 Model/Model.py

@@ -13,7 +13,8 @@ class Model:
 
     def __init__(self, forecast_days=1000):
         self._initialize_dependencies()
-        self._model_data = ModelData(forecast_days, self.dependency)
+        self._model_data = ModelData(forecast_days, self.dependency, True)
+        self.date = self.dependency.total_days
         # TODO: Initialize
         return
 
@@ -22,35 +23,39 @@ class Model:
         Firstly, we convert the number of newly infected cases to active cases
         """
         self.date += 1
-        self._model_data
+        # self._model_data
         self._model_transition()
         return
 
-    def _get_new_cases(self, cases, contact_type=(0, 0)):
+    def _get_new_cases(self, cases, contact_type=1):
         susceptibility = Parameters.sup_by_age
-        return np.matmul(self._model_data.dependency.matrix_by_class[contact_type[0]][contact_type[1]], cases)
+        matrix = self._synthesize_matrix(contact_type)
+        return np.matmul(matrix, cases)
 
     def _model_transition(self):
         self._exposed_to_cases(self.date)
-        self._infected_to_hospitalization(self.date)
-        self._hospitalized_to_icu(self.date)
-        self._infected_to_removed(self.date)
+        # self._infected_to_hospitalization(self.date)
+        # self._hospitalized_to_icu(self.date)
+        # self._infected_to_removed(self.date)
 
     def _exposed_to_cases(self, date):
         ratio = np.ones(shape=(16, 1), dtype=float)
 
         raw_kernel = Parameters.EXP2ACT_CONVOLUTION_KERNEL
-        kernel = np.matmul(ratio, np.transpose(raw_kernel.reshape((raw_kernel.shape[0], 1))))
+        kernel = np.matmul(raw_kernel.reshape((raw_kernel.shape[0], 1)), ratio.T)
         kernel_size = kernel.shape[0]
 
-        data = np.flip(self._time_series_active_cases[date - kernel_size:date], axis=0)
-        rslt = np.sum(np.multiply(data, kernel), axis=1)
-
-        self._time_series_active_cases[date] = rslt
-        self._time_series_clinical_cases[date] = np.multiply(rslt,
-                                                             Parameters.clinical_rate)
-        self._time_series_clinical_cases[date] = np.multiply(rslt,
-                                                             Parameters.subclinical_rate)
+        for i in range(Parameters.NO_COUNTY):
+            county_data = self._model_data._time_series_active_cases[i]
+            data = county_data[date - kernel_size:date]
[…]

### 2022-11-10 Model/ModelData.py

@@ -9,10 +9,12 @@ class ModelData:
         Attributes
     """
 
+    _forecast_days = 0
+
     _time_series_len = 0
 
     _time_series_infected = None
-    _time_series_exposed= None
+    _time_series_exposed = None
     _time_series_active_cases = None
     _time_series_clinical_cases = None
     _time_series_sub_clinical_cases = None
@@ -24,7 +26,7 @@ class ModelData:
 
     _time_series_immunity = None
 
-    def __init__(self, forecast_days=1000, dependency=None):
+    def __init__(self, forecast_days=1000, dependency=None, load_from_dependency=False):
         """
             Initialize the tensors
             shape=(x, y, z)
@@ -33,27 +35,57 @@ class ModelData:
             y = number of days to forecast + dates elapsed since Covid outbreak
             z = 16 age bands
         """
+        # TODO: Load data from
+        self._forecast_days = forecast_days
         self.dependency = dependency
         self._time_series_len = self.dependency.total_days + forecast_days
 
+        if load_from_dependency:
+            self._load_from_dependencies()
+        else:
+            x = len(self.dependency.county_data)
+            y = self._time_series_len
+            z = 16
+
+            # print(self._time_series_len)
+            self._time_series_infected = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_exposed = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_active_cases = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_clinical_cases = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_sub_clinical_cases = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_hospitalized = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_ICU = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_recovered = np.zeros(shape=(x, y, z), dtype=int)
+            self._time_series_deaths = np.zeros(shape=(x, y, z), dtype=int)
+
+            """
+                Note that!!! We asssumed an consistent vaccination level acrross ALL counties in ON!
+            """
+            self._time_series_vaccinated = np.zeros(shape=(y, z), dtype=int)
+
+            self._time_series_immunity = np.zeros(shape=(x, y, z), dtype=float)
+
+    def _load_from_dependencies(self):
         x = len(self.dependency.county_data)
-        y = self._time_series_len
[…]

### 2022-11-10 Model/Parameters.py

@@ -10,7 +10,19 @@ import datetime
 
 ver = '1.0'
 
+def find_mean(v):
+    tot = 0
+    for i in range(len(v)):
+        tot += v[i]
+        if tot >= 0.5:
+            print(i, len(v))
+            break
 
+def get_bayes(lst):
+    bayes = np.zeros(shape=lst.shape)
+    for i in range(lst.shape[0]):
+        bayes[i] = 1 / lst[i]
+    return bayes
 """
     Matrix constants
 """
@@ -59,16 +71,23 @@ ONT_DEATH_DISTRIBUTION = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 
 
 # susceptibility
 SUSP_BY_AGE = np.array([1, 2])
-# clinical ratio
-CLINICAL_BY_AGE = np.ones(shape=(16, 1), dtype=float)
 # subclinical ratio
-SUBCLINICAL_BY_AGE = np.zeros(shape=(16, 1), dtype=float)
+SUBCLINICAL_BY_AGE = np.array([0.750, 0.712, 0.683, 0.650, 0.616, 0.583, 0.550, 0.517, 0.483, 0.450, 0.417, 0.383,
+                            0.350, 0.317, 0.283, 0.250])
+# clinical ratio
+CLINICAL_BY_AGE = np.subtract(np.ones(shape=(16, ), dtype=float), SUBCLINICAL_BY_AGE)
 # critical rate
-CRIT_BY_AGE = np.zeros(shape=(16, 1), dtype=float)
+CRIT_BY_AGE = np.zeros(shape=(16,), dtype=float)
 # fatality rate (calculated)
-CFR_BY_AGE = np.zeros(shape=(16, 1), dtype=float)
+CFR_BY_AGE = np.zeros(shape=(16,), dtype=float)
 # fatality rate (calculated)
-EFFICACY_BY_AGE = np.zeros(shape=(16, 1), dtype=float)
+EFFICACY_BY_AGE = np.zeros(shape=(16,), dtype=float)
+
+"""
+    Bayes
+"""
+
+BAYES_CLINICAL_BY_AGE = get_bayes(CLINICAL_BY_AGE)
 
 # Work force
 LABOUR_FORCE_BY_AGE = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 0.106146399, 0.106351741,
[…]

### 2022-12-20 Model/Parameters.py
TODO: Need to update Parameters.py

@@ -121,19 +121,21 @@ VACCINE_AGE_BANDS = ['05-11yrs', '12-17yrs', '18-29yrs', '30-39yrs', '40-49yrs',
     These kernels are for 
 """
 
+EXP2ACT_RATIO = np.ones(shape=(16, ))
+
 kernel_size_1 = np.linspace(0, 12, 12)
 EXP2ACT_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_1, a=1.2, scale=4))
 ACT2CLI_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_1, a=1.2, scale=4))
 ACT2SUB_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_1, a=1.2, scale=4))
 
-"""
-    These kernels are for
-"""
-
 kernel_size_2 = np.linspace(0, 25, 25)
 SUB2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
 # TODO: CHECK IF THIS IS RIGHT?
 CLI2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
+
+
+# TODO: this is incorrect
+ICU2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
 
 """ 
     These kernels are for hospitalization, ICU, and deaths

### 2022-12-21 Model/Model.py
[*] Neew kernels.

@@ -178,7 +178,8 @@ class Model:
             county_data = self._model_data.time_series_clinical_cases[c]
             data = county_data[date - kernel_size:date]
             data = data[::-1]
-            rslt = np.sum(np.multiply(data, kernel), axis=0)
+            rslt_recover = np.sum(np.multiply(data, recover_kernel), axis=0)
+            rslt_death = np.sum(np.multiply(data, death_kernel), axis=0)
             self._model_data.time_series_recovered[c][date] = rslt
 
     def _synthesize_matrix(self, contact_type=0, contact_pattern='day'):

### 2022-12-21 Model/Parameters.py

@@ -2,6 +2,7 @@
     Version
 """
 from scipy.stats import gamma
+from scipy.stats import lognorm
 from Util import norm
 from Util import normalize
 import matplotlib.pyplot as plt
@@ -133,9 +134,10 @@ SUB2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
 # TODO: CHECK IF THIS IS RIGHT?
 CLI2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
 
-
 # TODO: this is incorrect
-ICU2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
+
+HOS2REC_CONVOLUTION_KERNEL = normalize(lognorm.pdf(range(0, 40), s=1.2, loc=11.08))
+ICU2REC_CONVOLUTION_KERNEL = normalize(lognorm.pdf(range(0, 40), s=1.25, loc=13.33))
 
 """ 
     These kernels are for hospitalization, ICU, and deaths

### 2022-12-21 Manuscripts/main.tex
Update

@@
 \usepackage{soul}
+
+% FONT
 \usepackage[charter,cal=cmcal]{mathdesign} % Specify font for serif family
@@
 \usepackage{sectsty} % Specify section formatting
-	\sectionfont{\sffamily\color{DarkBlue}}
-	\subsectionfont{\sffamily\color{LightBlue}}
-	\subsubsectionfont{\small\sffamily}
 
@@
 % \setmainfont{Arial}
-
+\usepackage{booktabs}  
 \newcommand{\urlref}{\hl{[REF]}}
@@
 \newcommand{\unknowndata}{\textcolor{ReD}{\textbf{\hl{$<$DATA$>$}}}$ \ $}
+\newcommand{\suppfigure}{{\textbf{\hl{$<$FIGURE$>$}}}$ \ $}
+\newcommand{\mainfigure}{\textcolor{ReD}{\textbf{\hl{$<$FIGURE$>$}}}$ \ $}
 
-\title{Supplementary Materials}
+\title{Predicting the transmission of COVID-19 using inter and intra-county mobility: a mathematical modelling study}
 \author{Blair Yang}
@@
 \begin{document}
+
+\maketitle
 
@@
 \pendingdata $ \ \ $ Pending data, need to be filled with data from the cited papers\\
-\unknowndata $ \ \ $ Pending data, need to be find relevant paper with such data
+\unknowndata $ \ \ $ Pending data, need to be find relevant paper with such data\\
+\mainfigure $ \ \ $ Pending main figure, need to be add a major figure for this section\\
+\suppfigure $ \ \ $ Pending supplementary figure, need to be add a supplementary figure in the supplementary material section for this section\\
+
+\mainfigure Essentially, the model takes in
+\begin{enumerate}
+    \item \important{PAST} Time-series data of the no. cases in Ontario in 26 PHUs
+    \item \important{PAST} Time-series data of the ratio of 1st, 2nd, and 3rd dose vaccination in Ontario
+    \item Labour force data and the commute matrix in Ontario
+    \item Contact Matrix and CoMix
+    \item \important{PREDICTED} Google mobility data in Ontario \emphasize{(Generated from NN)}
+    \item Epidemiological parameters
+    \item Vaccine parameters and time-series data of the \important{PREDICTED} immunity waning effects
+    \item Whether we use machine learning to address the
+\end{enumerate}
+and outputs
+\begin{itemize}
+    \item no. cases in each district
+    \item no. severe cases (ICU occupancy) in each district
+    \item no. deaths in each district
+\end{itemize}
 
 \section{Methodology (supplementary material)}
-\subsection{Data acquisition}
+\begin{center}
+    \includegraphics[width = 480pt]{Figure 1.jpg}
+\end{center}
+\textbf{Figure 1:} The epidemiological compartmental model.
+The transmission (infection) was divided into two stages: workplace and school, and household and others.
+\textbf{A).} Data calibration using time-series forecast.
+The Ontario-specific google mobility index, vaccination status, and current ratio of VOCs, were sent into a MLP network to forecast the trend in the following three years.
+\textbf{B).} The age-specific effective contact matrix synthesized from the relevant data output from the MLP network by categories.
+\textbf{C).} The susceptible compartment of the SEIR(S) model, stratified into 528 subgroups according to demographical data.
+The susceptible individuals in 528 counties will be redistributed by the starting of time-step 1 at the beginning of each transmission cycle due to commutation and will be restored by time-step 5.
+We assumed all of the removed individuals will be moved into the susceptible group 15 days after recovery with immunity (waning).
+\textbf{D).} The exposed and infected compartment of the model during the workplace and school transmission cycle.
+This stage uses synthesized workplace and school contact matrix, after redistribution due to commutation.
+\textbf{E).} The he exposed and infected compartment of the model during the household and others transmission cycle.
+This stage uses synthesized residence and others contact matrix, after restoration of commutation.
+\textbf{F).} The removed stage of the compartmental model.
+We assumed all of the recovered individuals will be move to susceptible state 15 days after recovery due to immunity waning.
+The recovered individual still has shielding immunity against infection.
+\subsection{Data source}
+
+\subsubsection{Demographic of Ontario}
+
+We stratified the population in Ontario into 26 public health units (PHU), \pendingdata districts, and 528 counties, and 16 age bands, according to the 2016 Canadian demographics census \pendingref.
+Our model...
+.
+The pool of susceptible individuals was divided into 528 counties, administrated by 26 PHUs.
+We assumed a uniformed incidence rate for the counties within the same PHU at on the first day of the modelling.
 
@@
 We acquired the provincial time-series vaccination data in Ontario from Ontario public health, covering the percentage population who has taken first does, second dose, and third does.
-We assumed a uniform distribution of the vaccination population ratio for every PHU.
+We assumed a uniform distribution of the vaccination ratio for every PHU.
 
@@
 
-The commuting data in Ontario was excerpted from the 2016 demographic census. We assumed a constant age distribution.
+The commuting matrix in Ontario was excerpted from the 2016 demographic census.
+We assumed a uniform age distribution across the province, and adjusted the number of commuters by \pendingdata due to the change in employment rate (\pendingdata).
+
+\subsubsection{Population mobility data}
+
+We used the population mobility data from Google.
+\unknownref The data was categorized into 5 groups: grocery and pharmacy, residential, retail and recreation, transit, and workplaces.
+To address the fluctuation of the population mobility, we used a multi-layer perceptive model (MLP) from Keras to forecast the population mobility in the next 1000 days since August 23rd, 2022.
+\cite{ref6} \pendingref
 
@@
 \hl{Source} suggested that there are significant underascertainment of the number of cases and deaths of COVID-19 in Canada.
-\cite{ref2} \cite{ref3} We calculated the average of the underascertainment ratio of \pendingdata and assumed the number to be constant throughout the pandemic.
+\cite{ref2} \cite{ref3} We calculated the average of the underascertainment ratio of \pendingdata and assumed the ratio to be constant throughout the pandemic.
 
@@
 
-\hl{Source} suggested that the waning effect of COVID-19 vaccine efficacy.
+Khoury and Menni suggested that the predictability of the immunity waning effect of COVID-19 vaccine.
+\cite{ref4} \cite{ref5} Menni's model gave an insight into the age-group specific vaccine efficacy of the most prevalence vaccines in Ontario, BNT162b2 and mRNA1273mm against infection for up to eight months.
+Khoury's model gave an estimation of the longer-term waning effect of the vaccine efficacy against both mild and severe symptoms.
+We \emphasize{combined two models} for both short-term and long-term accuracy.
+\mainfigure, \suppfigure.\\\\
+Ontario has announced its plan for third boost dose. $\cdots$ We also
+
+\subsection{Differential equations for the model}
+
+\begin{align*}
+     \text{Epidemiological} \ & \begin{cases}
+     dS(t) = - \sum_{x \in C} \vect{m_x \beta_0 \circ \vect{1_{16} - \mu} \vect{M^x}^T \vect{I_{t,c} + 0.5I_{t,s}}}\\
+        dE(t) = \sum_{x \in C} \vect{m_x \beta_0 \circ \vect{1_{16} - \mu} \vect{M^x}^T \vect{I_{t,c} + 0.5I_{t,s}}} - dI\\
+        dI_s(t) = \sum_{d \leq t} \vect{v \circ E_d \sigma (t - d) - \gamma_{s}I_s} - dR_s(t)\\
+         dI_c(t) = \sum_{d \leq t} \vect{ \vect{1_{16} - v} \circ E_d \sigma (t - d) - \gamma_{s}I_s} - dR_c(t)\\
+        dI_{hosp} (t) =  \vect{\sum_{d \leq t} I_{i,d} h(i) \vect{1 - g(i)}  T_{hosp}(t - d) }_{i}^{i \in \text{age bands}}\\
+        dI_{ICU}(t) = \vect{\sum_{d \leq t} I_{hosp, d} g(i) T_{ICU}(t - d) }_{i}^{i \in \text{age bands}}\\
+         dI_{non-hosp}(t) =  d I_{c} - d I_{hosp,  t}- d I_{ICU, t} - dR_{ICU}\\
+         dI(t) = dI_s(t) + dI_{non-hosp}(t) + dI_{hosp}(t) + dI_{ICU}(t)\\
+         d R_{s}(t) = \sum_{d \leq t} I_s\gamma_s(t-d)\\
+         d R_{non-hosp}(t) = \sum_{d \leq t} I_{non-hosp} \gamma_{non-hosp}(t-d)\\
+         d R_{hosp}(t) = \sum_{d \leq t} I_{hosp} \gamma_{hosp}(t-d)\\
+         d R_{ICU}(t) = \sum_{d \leq t} I_{ICU} \gamma_{ICU}(t-d)\\
+         dR(t) = dR_s (t) + d R_{non-hosp}(t) +d R_{hosp}(t) + d R_{ICU}(t)\\
+    d D (t) = cfr \circ dR(t)\\
+    d r (t) = \vect{1_{16} - cfr} \circ dR(t)\\
+     \mu_{t,v,s} = \frac{\sum_{d \leq t} V_d \varphi(t - d)\mu_{0,v,s}}{P}\\
+         \mu_{t,n,s} = \frac{\sum_{d \leq t} I_d \varphi(t - d)\mu_{0,v,s}}{P}\\
+         \mu_{t,s} = \frac{\sum_{d \leq t} I_d \varphi(t - d)\mu_{0,v,s} +  \sum_{d \leq t} V_d \varphi(t - d)\mu_{0,v,s}}{P}\\
+         cfr = cfr_0 \circ \mu_{t,s}
+     \end{cases}\\
+     \text{Commutational} \ & \begin{cases}
+     out_{c,t, I} = {I_{c,t} \circ w}\\
+        out_{c,t, S} = {S_{c,t} \circ w}\\
+        OUT_{c,t,I} = \vect{\frac{C_{i,j}}{sum\vect{C_i}} out_{c,t,I}}_{j}^{j \in \set{1, \cdots, 528}}\\
+        OUT_{c,t,S} = \vect{\frac{C_{i,j}}{sum\vect{C_i}} out_{c,t,S}}_{j}^{j \in \set{1, \cdots, 528}}
+     \end{cases}
+\end{align*}
+
+\newpage 
+\subsection{Parameters}
+
+\begin{center}
+    \begin{table}[h]
+    \caption{Parameters that are not subject to fitting}
+    \centering
+\begin{tabular}[H]{p{2cm}p{4cm}p{4cm}p{5cm}}
+     \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
+     \midrule
+     $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$; days) & $\sim gamma(2.5,4)$& Set to 2.5 so that incubation period (latent period plus period of preclinical infectiousness) is 5 days\\
+     $d_p$ & Duration of pre-clinical infectiousness& $\sim gamma(2.5,4)$ &  \\
+     $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  \\
+     $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  \\
+     $d_I$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ &  
+\end{tabular}
+\end{table}
+\end{center}
+
+\begin{align*}
+    P(Hosp|Clinical) = /
+\end{align*}
+We defined following variables with their corresponding meaning. Each variable is a real-valued function $\cdot: \text{date} \to \R^+$.
+\begin{align*}
+    S & := \ \text{Number of susceptible individuals}\\
+    E & := \ \text{Number of exposed individuals}\\
+    I & := \ \text{Number of infected individuals}\\
+    I_s &:= \text{Number of subclinical infected individuals}\\
+    I_p &:= \text{Number of preclinical infected individuals}\\
+    I_c &:= \text{Number of clinical infected individuals}\\
+    I_h &:= \text{Number of hospitalized infected individuals}\\
+    I_{ICU} &:= \text{Number of ICU-hospitalized infected individuals}\\
+    R & := \ \text{Number of removed individuals}\\
+    r & := \ \text{Number of recovered individuals}\\
+    D & := \ \text{Number of deceased individuals}\\ 
+\end{align*}
+We define the following notations to represent the change of variables:
+\begin{align*}
+    \Delta \ \cdot &:= \ \text{Number of individuals transformed into a specific state within a time step}\\
+    \delta \ \cdot &:= \ \text{Number of individuals transformed out from a specific state within a time step}\\
+    d \ \cdot &:= \ \text{chahnge of the number of individuals transformed out from a specific state within a time step}\\
+\end{align*}
+We define the following transition functions:
+\subsection*{Susceptible to exposed}
+\begin{align*}
+    \Delta S(t) &= \overbrace{\vect{\Delta R(t) - \Delta D(t)}}^{= \Delta r(t)}\\
+    \delta S(t) &= - \Delta E(t)\\
+    dS(t) &=  \Delta S(t) - \delta S(t) = \overbrace{\vect{\Delta R(t) - \Delta D(t)}}^{= \Delta r(t)} - \Delta E
+\end{align*}
+
+\subsection*{Exposed to infected}
+\subsubsection*{Exposed to subclinically-infected}
+\begin{align*}
+    \Delta I_s(t) &= \vect{E * f_{d_s}  }(t) \circ  sub\_ratio \\
+    \delta I_s(t) &= \vect{I_s * f_{d_{s}}} (t) \\
+    d I_s(t) &=  \Delta I_s(t)  -  \delta I_s (t)
+\end{align*}
+
+\subsubsection*{Exposed to pre-clinically infected}
+\begin{align*}
+    \Delta I_p(t) &= \vect{E * f_{d_p} }(t) \circ  cli\_ratio \\
+    \delta I_p(t) &= \vect{I_p(t) * f_{d_{c}}} (t) \\
+    d I_p(t) &=  \Delta I_p (t)  -  \delta I_p (t)
+\end{align*}
+
+\subsection*{Exposed to all-type of infected indeviduals}
+\begin{align*}
+    \Delta I &= \Delta I_s + \Delta I_p\\
+    \delta I &= \delta I_s + \delta I_p\\
+    d I &= d I_s + d I_p\\
+\end{align*}
+
+\subsection*{Transition within infected}
+\subsubsection*{Pre-clinical infected to clinical infected}
+\begin{align*}
+    \Delta I_c &= \vect{I_p * f_{d_c}} (t)\\
+    \delta I_c &= \vect{I_c * f_{d_r - d_c}} (t)\\
+\end{align*}
 
@@
 CMAJ Open, 10(3).
-https://doi.org/10.9778/cmajo.20220031 }
+https://doi.org/10.9778/cmajo.20220031}
+
+\bibitem{ref4}{Khoury, D.
+S., Cromer, D., Reynaldi, A., Schlub, T.
+E., Wheatley, A.
+K., Juno, J.
+A., Subbarao, K., Kent, S.
+J., Triccas, J.
+A., $\&$ Davenport, M.
+P.
+(2021).
+Neutralizing antibody levels are highly predictive of immune protection from symptomatic SARS-CoV-2 infection.
+Nature Medicine.
+https://doi.org/10.1038/s41591-021-01377-8}
+
+\bibitem{ref5}{Menni, C., May, A., Polidori, L., Louca, P., Wolf, J., Capdevila, J., Hu, C., Ourselin, S., Steves, C.
+J., Valdes, A.
+M., $\&x$amp; Spector, T.
+D.
+(2022).
+Covid-19 vaccine waning and effectiveness and side-effects of boosters: A Prospective Community study from the Zoe Covid Study.
+The Lancet Infectious Diseases, 22(7), 1002–1010.
+https://doi.org/10.1016/s1473-3099(22)00146-3}
+
+\bibitem{ref6}{https://github.com/keras-team/keras}
+
+\bibitem{ref7}{10.1001/jama.2022.2274}
 \end{thebibliography}

### 2022-12-21 Model/Model.py

@@ -129,12 +129,11 @@ class Model:
             data = county_data[date - kernel_size:date]
             data = data[::-1]
             rslt = np.sum(np.multiply(data, kernel), axis=0)
-            self._model_data.time_series_recovered[c][date] = rslt
+            self._model_data.time_series_recovered[c][date] += rslt
 
     def _clinical_to_removed(self, date):
         # All non-hospitalized cases recvovers
         ratio = np.ones(shape=(16, 1)) - Parameters.ONT_HOSP_RATIO.reshape(16, 1)
-        # TODO: Check kernel!
         raw_kernel = Parameters.CLI2REC_CONVOLUTION_KERNEL
         kernel = np.matmul(raw_kernel.reshape((raw_kernel.shape[0], 1)), ratio.T)
         kernel_size = kernel.shape[0]
@@ -144,35 +143,22 @@ class Model:
             data = county_data[date - kernel_size:date]
             data = data[::-1]
             rslt = np.sum(np.multiply(data, kernel), axis=0)
-            self._model_data.time_series_recovered[c][date] = rslt
+            self._model_data.time_series_recovered[c][date] += rslt
 
 
     def _hospitalized_to_removed(self, date):
-        # hospitalized cases my decease, or recov3er
-        ratio = np.ones(shape=(16, 1))
+        # hospitalized cases may decease, or recover
+        death_ratio = (Parameters.ONT_CFR / Parameters.ONT_HOSP_RATIO).reshape(16, 1)
+        recovery_ratio = np.ones(shape=(16, 1)) - death_ratio
         # TODO: Change kernel!
         # TODO: Patients may die in this stage, update!
-        raw_kernel = Parameters.CLI2REC_CONVOLUTION_KERNEL
-        raw_kernel_2 = Parameters.CLI2
-        kernel = np.matmul(raw_kernel.reshape((raw_kernel.shape[0], 1)), ratio.T)
-        kernel_size = kernel.shape[0]
 
-        for c in range(Parameters.NO_COUNTY):
-            county_data = self._model_data.time_series_clinical_cases[c]
-            data = county_data[date - kernel_size:date]
-            data = data[::-1]
-            rslt = np.sum(np.multiply(data, kernel), axis=0)
-            self._model_data.time_series_recovered[c][date] = rslt
+        recover_kernel = Parameters.HOS2RMV_CONVOLUTION_KERNEL
[…]

### 2022-12-21 Model/Parameters.py

@@ -1,6 +1,8 @@
 """
     Version
 """
+import math
+
 from scipy.stats import gamma
 from scipy.stats import lognorm
 from Util import norm
@@ -125,40 +127,39 @@ VACCINE_AGE_BANDS = ['05-11yrs', '12-17yrs', '18-29yrs', '30-39yrs', '40-49yrs',
 EXP2ACT_RATIO = np.ones(shape=(16, ))
 
 kernel_size_1 = np.linspace(0, 12, 12)
+
 EXP2ACT_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_1, a=1.2, scale=4))
 ACT2CLI_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_1, a=1.2, scale=4))
 ACT2SUB_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_1, a=1.2, scale=4))
 
+kernel_size_3 = np.linspace(0, 15, 15)
+INF2HOS_CONVOLUTION_KERNEL = normalize(norm(kernel_size_3, mean=7.5, scale=1))
+HOS2ICU_CONVOLUTION_KERNEL = normalize(norm(kernel_size_3, mean=11.1 - 7.5, scale=1))
+HOS2DEA_CONVOLUTION_KERNEL = normalize(norm(kernel_size_3, mean=7.5, scale=math.sqrt(5)))
+
 kernel_size_2 = np.linspace(0, 25, 25)
 SUB2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
-# TODO: CHECK IF THIS IS RIGHT?
 CLI2REC_CONVOLUTION_KERNEL = normalize(gamma.pdf(kernel_size_2, a=1.6, scale=4))
 
 # TODO: this is incorrect
 
-HOS2REC_CONVOLUTION_KERNEL = normalize(lognorm.pdf(range(0, 40), s=1.2, loc=11.08))
-ICU2REC_CONVOLUTION_KERNEL = normalize(lognorm.pdf(range(0, 40), s=1.25, loc=13.33))
+"""
+    Average stay in hospital and ICU
+"""
+HOS2RMV_CONVOLUTION_KERNEL = normalize(lognorm.pdf(range(0, 40), s=1.2, loc=11.08))
[…]

### 2022-12-21 Manuscripts/main.tex
Update latex

@@
     \begin{table}[h]
-    \caption{Parameters that are not subject to fitting}
+    \caption{Convolutional kernels in the model as probability distributions}
     \centering
-\begin{tabular}[H]{p{2cm}p{4cm}p{4cm}p{5cm}}
+\begin{tabular}[H]{p{2cm}p{6cm}p{4cm}p{4cm}}
      \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
@@
      $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  \\
-     $d_I$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ &  
+     $d_{pos}$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ & \\ 
+     $d_{hosp}$ & Duration from PCR positivity to hospitalization& $\sim normal(7.5, 1)$ & \\ 
+     $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & \\ 
 \end{tabular}

### 2022-12-21 Manuscripts/main.tex
Todo: update the kernels

@@
      $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & \\ 
+     $d_{R,hosp}$ & Average stay in hospital& $\sim normal(3.6, 1)$ & \\ 
+     $d_{R,ICU}$ & Average stay in ICU & $\sim normal(3.6, 1)$ & \\ 
 \end{tabular}

### 2022-12-21 Manuscripts/main.tex
New prob dist

--- 2022-12-21 Manuscripts/main.tex
@@
      \midrule
-     $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$; days) & $\sim gamma(2.5,4)$& Set to 2.5 so that incubation period (latent period plus period of preclinical infectiousness) is 5 days\\
-     $d_p$ & Duration of pre-clinical infectiousness& $\sim gamma(2.5,4)$ &  \\
+     $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$) & $\sim gamma(2.5,4)$ & Davies et al.\\
      $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  \\
@@
      $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & \\ 
+     $d_{R,hosp}$ & Average stay in hospital& $\sim normal(11.08, 1.2)$ & \\ 
+     $d_{R,ICU}$ & Average stay in ICU & $\sim normal(3.6, 1)$ & \\ 
 \end{tabular}

### 2022-12-22 Manuscripts/main.tex
Update model

@@
     \centering
-\begin{tabular}[H]{p{2cm}p{6cm}p{4cm}p{4cm}}
+\begin{tabular}[H]{p{2cm}p{6cm}p{4cm}p{3cm}}
      \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
@@
      $d_E$ & Latent period ($E$ to $I_p$ and $E$ to $I_s$) & $\sim gamma(2.5,4)$ & Davies et al.\\
-     $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  \\
-     $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  \\
-     $d_{pos}$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ & \\ 
-     $d_{hosp}$ & Duration from PCR positivity to hospitalization& $\sim normal(7.5, 1)$ & \\ 
-     $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & \\ 
-     $d_{R,hosp}$ & Average stay in hospital& $\sim normal(11.08, 1.2)$ & \\ 
-     $d_{R,ICU}$ & Average stay in ICU & $\sim normal(3.6, 1)$ & \\ 
+     $d_c$ & Duration of clinical infectiousness& $\sim gamma(2.5,4)$ &  Davies et al.\\
+     $d_s$ & Duration of sub-clinical infectiousness& $\sim gamma(5,4)$ &  Davies et al.\\
+     $d_{pos}$ & Duration of PCR positivity& $\sim normal(9.87, 0.25)$ & [REF]\\ 
+     $d_{hosp}$ & Duration from PCR positivity to hospitalization& $\sim normal(7.5, 1)$ & Davies et al.\\ 
+     $d_{ICU}$ & Duration from hospitalization to ICU& $\sim normal(3.6, 1)$ & Davies et al.\\ 
+     $d_{R,hosp}$ & Average stay in hospital & $\sim normal(11.08, 1.2)$ & Davies et al.\\ 
+     $d_{R,ICU}$ & Average stay in hospital & $\sim normal(13.33, 1.2)$ & Davies et al.
     \end{tabular}
@@
 \end{center}
+
+\begin{center}
+    \begin{table}[h]
+    \caption{Age-specific odds}
+    \centering
+\begin{tabular}[H]{p{3cm}p{5cm}p{4cm}p{3cm}}
+     \textbf{Parameter}& \textbf{Description}  & \textbf{Value}& \textbf{Reference} \\
+     \midrule
+     $susc\_ratio$ & Relative susceptibility to infection by age & 0.39 - 0.86 & Davies et al.\\
+     $clin\_ratio$ & Clinical fraction by age &  0.23 - 0.71  &  Davies et al.\\
+     $hosp\_ratio$ & Hospitalization ratio of clinical cases by age & 0.009 - 0.21 &  [REF]\\
+     $icu\_ratio$ & ICU hospitalized ratio of clinical cases by age & 0.001 - 0.028 &  [REF]\\
+     $cfr\_ratio$ & Case-fatality ratio by age& 0.00009 - 0.09 &  [REF]\\
+     $work\_ratio$ & Working force ratio by age& DoG interpolation &  [REF]\\
+     $sch\_ratio$ & School ratio by age & DoG interpolation &  [REF]
+    \end{tabular}
+\end{table}
+\end{center}
+
+\newpage
 
@@
 \begin{align*}
+    \Delta E (t) &= susc_ratio \circ M^x I(x)
+\end{align*}
+\begin{align*}
     \Delta S(t) &= \overbrace{\vect{\Delta R(t) - \Delta D(t)}}^{= \Delta r(t)}\\
@@
 \subsection*{Exposed to infected}
-\subsubsection*{Exposed to subclinically-infected}
+\subsubsection*{Exposed to subclinical infection}
 \begin{align*}
-    \Delta I_s(t) &= \vect{E * f_{d_s}  }(t) \circ  sub\_ratio \\
-    \delta I_s(t) &= \vect{I_s * f_{d_{s}}} (t) \\
-    d I_s(t) &=  \Delta I_s(t)  -  \delta I_s (t)
+    \Delta I_s(t) &= \vect{E * f_{d_s}  }(t) \circ \vect{1_{16} - clin\_ratio} \\
+    \delta I_s(t) &= \vect{I_s * f_{d_{s}}} (t)
 \end{align*}
 
-\subsubsection*{Exposed to pre-clinically infected}
+\subsubsection*{Exposed to pre-clinical infection}
 \begin{align*}
-    \Delta I_p(t) &= \vect{E * f_{d_p} }(t) \circ  cli\_ratio \\
-    \delta I_p(t) &= \vect{I_p(t) * f_{d_{c}}} (t) \\
-    d I_p(t) &=  \Delta I_p (t)  -  \delta I_p (t)
+    \Delta I_p(t) &= \vect{E * f_{d_p} }(t) \circ  clin\_ratio \\
+    \delta I_p(t) &= \vect{I_p(t) * f_{d_{c}}} (t)
 \end{align*}
@@
     \delta I &= \delta I_s + \delta I_p\\
-    d I &= d I_s + d I_p\\
+    d S(t) &= \vect{\Delta I_s + \Delta I_p } - \vect{\delta I_s + \delta I_p}
 \end{align*}
@@
 \subsection*{Transition within infected}
-\subsubsection*{Pre-clinical infected to clinical infected}
+\subsubsection*{Pre-clinical infection to clinical infection}
 \begin{align*}
     \Delta I_c &= \vect{I_p * f_{d_c}} (t)\\
-    \delta I_c &= \vect{I_c * f_{d_r - d_c}} (t)\\
+    \delta I_c &= \vect{I_c * f_{d_{pos}}} (t)
 \end{align*}

### 2022-12-22 Model/Model.py

@@ -52,13 +52,13 @@ class Model:
             active_transmissible = self._model_data.time_series_clinical_cases[c][date]
             # immunity_level = np.zeros(shape=(16, ))
             immunity_level = self._model_data.time_series_immunity[c][date]
-            immunity_coeff = np.ones(shape=(16, )) - immunity_level
+            immunity_coeff = np.ones(shape=(16,)) - immunity_level
             self._get_new_cases(np.multiply(exposed_cases + active_transmissible, immunity_coeff))
-
 
     """
         Exposed to cases
     """
+
     def _exposed_to_cases(self, date):
         ratio = Parameters.SUSC_BY_AGE.reshape(16, 1)
 
@@ -94,6 +94,21 @@ class Model:
             rslt = np.sum(np.multiply(data, kernel), axis=0)
             self._model_data.time_series_hospitalized[c][date] = rslt
 
+    def _infected_to_death(self, date):
+        ratio = Parameters.ONT_CFR.reshape(16, 1)
+        raw_kernel = Parameters.CLI2DEA_CONVOLUTION_KERNEL
+        kernel = np.matmul(raw_kernel.reshape((raw_kernel.shape[0], 1)), ratio.T)
+        kernel_size = kernel.shape[0]
+
+        for c in range(Parameters.NO_COUNTY):
+            county_data = self._model_data.time_series_clinical_cases[c]
+            data = county_data[date - kernel_size:date]
+            data = data[::-1]
+            rslt = np.sum(np.multiply(data, kernel), axis=0)
+            self._model_data.time_series_deaths[c][date] = rslt
+
+
+        return
 
     def _hospitalized_to_icu(self, date):
         ratio = (Parameters.ONT_ICU_RATIO / Parameters.ONT_HOSP_RATIO).reshape(16, 1)
@@ -132,8 +147,8 @@ class Model:
             self._model_data.time_series_recovered[c][date] += rslt
 
     def _clinical_to_removed(self, date):
-        # All non-hospitalized cases recvovers
-        ratio = np.ones(shape=(16, 1)) - Parameters.ONT_HOSP_RATIO.reshape(16, 1)
+        ratio = np.ones(shape=(16, 1))
+
         raw_kernel = Parameters.CLI2REC_CONVOLUTION_KERNEL
         kernel = np.matmul(raw_kernel.reshape((raw_kernel.shape[0], 1)), ratio.T)
         kernel_size = kernel.shape[0]
[…]

### 2022-12-22 Model/Parameters.py

@@ -5,7 +5,7 @@ import math
 
 from scipy.stats import gamma
 from scipy.stats import lognorm
-from Util import norm
+from scipy.stats import norm
 from Util import normalize
 import matplotlib.pyplot as plt
 import numpy as np
@@ -82,9 +82,8 @@ ONT_CFR = np.array([9.87293737e-05, 9.63117654e-05, 9.62190186e-05, 1.30947921e-
                     3.32161024e-03, 5.97837815e-03, 1.13594029e-02, 2.04377866e-02, 3.74666196e-02,
                     9.35947229e-02])
 
-
 # susceptibility
-SUSC_BY_AGE = np.array([3.991327254652800027e-01, 3.948075309394725174e-01, 4.022340898538860898e-01,
+SUSC_RATIO = np.array([3.991327254652800027e-01, 3.948075309394725174e-01, 4.022340898538860898e-01,
                         4.963382577801381812e-01, 6.774025858086478724e-01, 7.930450307450174208e-01,
                         8.374194527357667894e-01, 8.402912936299908875e-01, 8.176304599317949506e-01,
                         8.081257676036830429e-01, 8.168620238480317486e-01, 8.359357113555672125e-01,
@@ -92,18 +91,17 @@ SUSC_BY_AGE = np.array([3.991327254652800027e-01, 3.948075309394725174e-01, 4.02
                         7.715186068117150242e-01
                         ])
 
-CLINICAL_BY_AGE = np.array([0.2865309, 0.26724745, 0.22402391, 0.15445847, 0.07258315, 0.10150448, 0.2401337,
-                               0.33644525, 0.38357917, 0.42265894, 0.47025061, 0.52584302, 0.59291004, 0.64122657,
-                               0.67295434, 0.71677774])
+CLINICAL_RATIO = np.array([0.2865309, 0.26753682, 0.23495708, 0.23019938, 0.25561971, 0.28454104,
+                            0.31587461, 0.34737841, 0.38386853, 0.42265894, 0.47025061, 0.52584302,
[…]

### 2022-12-23 Model/Dependency.py
[*] Update, now runable.

@@ -20,6 +20,10 @@ class Dependency:
     county_codes = list()
     matrix_by_class = [[None] * 4, [None] * 4]
 
+    """
+        Look up table
+    """
+
     code_to_name = dict()
     district_to_phu = dict()
     phu_to_district = dict()
@@ -27,11 +31,19 @@ class Dependency:
     county_to_district = dict()
     district_to_county = dict()
 
+    """
+        PHU-specific data
+    """
+
     band_to_population = dict()
     date_to_incidence_rate_by_phu = dict()
     date_to_hospitalization_rate_by_phu = dict()
     date_to_death_rate_by_phu = dict()
     date_to_vaccines_by_age = np.zeros((0, 3, 9))
+
+    """
+        County-specific data
+    """
 
     date_to_cases_by_county = None
     date_to_hospitalizations_by_county = None

### 2022-12-23 Model/Model.py

@@ -29,7 +29,7 @@ class Model:
         return
 
     def _get_new_cases(self, cases, contact_type=0, contact_pattern='day'):
-        susceptibility = Parameters.SUSC_BY_AGE
+        susceptibility = Parameters.SUSC_RATIO
         matrix = self._synthesize_matrix(contact_type, contact_pattern)
         self._model_data.compute_immunity(self.date)
         # print(self._model_data.time_series_immunity.shape)
@@ -60,22 +60,24 @@ class Model:
     """
 
     def _exposed_to_cases(self, date):
-        ratio = Parameters.SUSC_BY_AGE.reshape(16, 1)
+        ratio = Parameters.SUSC_RATIO.reshape(16, 1)
 
         raw_kernel = Parameters.EXP2ACT_CONVOLUTION_KERNEL
-        kernel = np.matmul(raw_kernel.reshape((raw_kernel.shape[0], 1)), ratio.T)
-        kernel_size = kernel.shape[0]
 
         for c in range(Parameters.NO_COUNTY):
+            immunity_level = self._model_data.time_series_immunity[c][date]
+            ratio *= immunity_level.reshape(16, 1)
+            kernel = np.matmul(raw_kernel.reshape((raw_kernel.shape[0], 1)), ratio.T)
+            kernel_size = kernel.shape[0]
             county_data = self._model_data.time_series_exposed[c]
             data = county_data[date - kernel_size:date]
             data = data[::-1]
             rslt = np.sum(np.multiply(data, kernel), axis=0)
             self._model_data.time_series_active_cases[c][date] = rslt
             self._model_data.time_series_clinical_cases[c][date] = np.multiply(rslt,
-                                                                               Parameters.CLINICAL_BY_AGE)
+                                                                               Parameters.CLINICAL_RATIO)
             self._model_data.time_series_clinical_cases[c][date] = np.multiply(rslt,
-                                                                               Parameters.SUBCLINICAL_BY_AGE)
+                                                                               Parameters.SUBCLINICAL_RATIO)
 
     def _infected_to_hospitalized(self, date):
 
@@ -178,7 +180,7 @@ class Model:
 
         ratio = np.ones(shape=(16, 1))
 
-        raw_kernel = Parameters.ICU2DEA_CONVOLUTION_KERNEL
+        raw_kernel = Parameters.ICU2RMV_CONVOLUTION_KERNEL
[…]

### 2022-12-23 Model/ModelData.py

@@ -88,8 +88,13 @@ class ModelData:
 
         self.time_series_sub_clinical_cases = self.time_series_active_cases - self.time_series_clinical_cases
 
-        self.time_series_deaths = np.concatenate([self.dependency.date_to_deaths_by_county,
-                                                  np.zeros(shape=(x, y, z))], axis=1)
+        # TODO: update this
+
+        self.time_series_recovered = np.apply_along_axis(lambda m:
+                                                         np.convolve(m,
+                                                                     Parameters.CLI2REC_CONVOLUTION_KERNEL,
+                                                                     mode='same'), axis=1,
+                                                         arr=self.time_series_clinical_cases)
 
         self.time_series_deaths = np.concatenate([self.dependency.date_to_deaths_by_county,
                                                   np.zeros(shape=(x, y, z))], axis=1)

### 2022-12-23 Model/Model.py
Still bugs in immunity computation. Otherwise it's all good.

@@ -26,18 +26,9 @@ class Model:
         print(self.date)
         self._model_data.compute_immunity(self.date)
         self._model_transition()
+        today_cases = self._model_data.time_series_active_cases.transpose(1, 0, 2)
+        print(np.sum(today_cases[self.date]))
         return
-
-    def _get_new_cases(self, cases, contact_type=0, contact_pattern='day'):
-        susceptibility = Parameters.SUSC_RATIO
-        matrix = self._synthesize_matrix(contact_type, contact_pattern)
-        self._model_data.compute_immunity(self.date)
-        # print(self._model_data.time_series_immunity.shape)
-        immunity = self._model_data.time_series_immunity.transpose(1, 0, 2)[self.date]
-        # print(immunity.shape)
-        rslt = np.matmul(matrix, cases) * susceptibility * immunity
-        # print(rslt.shape)
-        return rslt
 
     def _model_transition(self):
         self._susceptible_to_exposed(self.date)
@@ -46,33 +37,50 @@ class Model:
         self._hospitalized_to_icu(self.date)
         self._infected_to_removed(self.date)
 
+    def _get_new_cases(self, cases, contact_type=0, contact_pattern='day'):
+        susceptibility = Parameters.SUSC_RATIO
+        matrix = self._synthesize_matrix(contact_type, contact_pattern)
+        rslt = np.matmul(matrix, cases) * susceptibility
+        return rslt
+
     def _susceptible_to_exposed(self, date):
+        # self._model_data.compute_immunity(self.date)
         for c in range(Parameters.NO_COUNTY):
-            exposed_cases = self._model_data.time_series_exposed[c][date]
-            active_transmissible = self._model_data.time_series_clinical_cases[c][date]
-            # immunity_level = np.zeros(shape=(16, ))
-            immunity_level = self._model_data.time_series_immunity[c][date]
-            immunity_coeff = np.ones(shape=(16,)) - immunity_level
-            self._get_new_cases(np.multiply(exposed_cases + active_transmissible, immunity_coeff))
+            exposed_cases = self._model_data.time_series_exposed[c][date-1]
+            active_transmissible = self._model_data.time_series_clinical_cases[c][date-1]
+            immunity_level = self._model_data.time_series_immunity[c][date-1]
+            immunity = np.ones(shape=(16,)) - immunity_level
+
[…]

### 2022-12-23 Model/ModelData.py

@@ -16,6 +16,7 @@ class ModelData:
     time_series_len = 0
 
     time_series_infected = None
+    time_series_incidence = None
     time_series_exposed = None
     time_series_active_cases = None
     time_series_clinical_cases = None
@@ -24,6 +25,7 @@ class ModelData:
     time_series_ICU = None
     time_series_recovered = None
     time_series_deaths = None
+    time_series_population = None
 
     time_series_immunized = None
     time_series_vaccinated = None
@@ -54,7 +56,7 @@ class ModelData:
             y = self._time_series_len
             z = 16
 
-            # print(self._time_series_len)
+            self.time_series_population = np.zeros(shape=(x, y, z), dtype=int)
             self.time_series_infected = np.zeros(shape=(x, y, z), dtype=int)
             self.time_series_exposed = np.zeros(shape=(x, y, z), dtype=int)
             self.time_series_active_cases = np.zeros(shape=(x, y, z), dtype=int)
@@ -76,6 +78,7 @@ class ModelData:
         x = len(self.dependency.county_data)
         y = self.forecast_days
         z = 16
+
         self.time_series_clinical_cases = np.concatenate([self.dependency.date_to_cases_by_county,
                                                           np.zeros(shape=(x, y, z))], axis=1)
 
@@ -110,12 +113,9 @@ class ModelData:
 
         self.time_series_vaccinated = self.time_series_vaccinated.transpose(1, 0, 2)
 
-        print(self.time_series_vaccinated.shape)
 
-        self.time_series_immunized = np.zeros(shape=(x, self.time_series_len, z), dtype=float)
-        self.time_series_immunity = np.zeros(shape=(x, self.time_series_len, z), dtype=float)
-
-        # self.time_series_immunized = self.time_series_active_cases + 0.9 * self.time_series_vaccinated
+        self.time_series_immunized = np.zeros(shape=(x, y, z), dtype=float)
+        self.time_series_immunity = np.zeros(shape=(x, y, z), dtype=float)
 
     def compute_immunity(self, date):
         """
@@ -129,29 +129,71 @@ class ModelData:
         dose2 = np.clip((self.time_series_vaccinated[1] - self.time_series_vaccinated[2])[:date], a_min=0, a_max=1)
         dose3 = (self.time_series_vaccinated[2])[:date]
 
[…]

### 2022-12-23 Model/ModelData.py
Fixed immunity computation, one more inference to go.

@@ -164,15 +164,18 @@ class ModelData:
         raw_kernel_dose_3 = Parameters.VACCINE_EFFICACY_KERNEL_DOSE3[::-1]
         raw_kernel_infection = Parameters.INFECTION_EFFICACY_KERNEL[::-1]
 
-        kernel_dose_1 = raw_kernel_dose_1[:date].reshape(date, 1)
-        kernel_dose_2 = raw_kernel_dose_2[:date].reshape(date, 1)
-        kernel_dose_3 = raw_kernel_dose_3[:date].reshape(date, 1)
-        kernel_infection = raw_kernel_infection[:date].reshape(date, 1)
+        ratio = np.ones(shape=(1, Parameters.NO_COUNTY, 16))
+        kernel_dose_1 = np.multiply(raw_kernel_dose_1[:date].reshape(date, 1, 1), ratio)
+        kernel_dose_2 = np.multiply(raw_kernel_dose_2[:date].reshape(date, 1, 1), ratio)
+        kernel_dose_3 = np.multiply(raw_kernel_dose_3[:date].reshape(date, 1, 1), ratio)
+        kernel_infection = np.multiply(raw_kernel_infection[:date].reshape(date, 1, 1), ratio)
 
-        immunity_dose1 = np.multiply(dose1.T, kernel_dose_1)
-        immunity_dose2 = np.multiply(dose2.T, kernel_dose_2)
-        immunity_dose3 = np.multiply(dose3.T, kernel_dose_3)
-        immunity_infection = np.multiply(today_incidence.T, kernel_infection)
+        print(kernel_dose_1.shape)
+
+        immunity_dose1 = np.multiply(dose1, kernel_dose_1)
+        immunity_dose2 = np.multiply(dose2, kernel_dose_2)
+        immunity_dose3 = np.multiply(dose3, kernel_dose_3)
+        immunity_infection = np.multiply(today_incidence, kernel_infection)
 
         print('HOLY!')
         print(np.max(immunity_infection))

### 2022-12-23 Model/Dependency.py
TODO added.

@@ -301,7 +301,15 @@ class Dependency:
                     yesterday_cuml = today_cuml
 
         """
+
+        dose1 = np.clip((self.date_to_vaccines_by_age[0] - self.date_to_vaccines_by_age[1]), a_min=0, a_max=1)
+        dose2 = np.clip((self.date_to_vaccines_by_age[1] - self.date_to_vaccines_by_age[2]), a_min=0, a_max=1)
+        dose3 = (self.date_to_vaccines_by_age[2])
+
         for i in range(self.total_days - 1):
+
+            # TODO: CHANGE THIS!!!!
+
             vaccine_differentiated[i+1] = self.date_to_vaccines_by_age[i+1] - self.date_to_vaccines_by_age[i]
         self.date_to_vaccines_by_age = np.clip(vaccine_differentiated, a_min=0, a_max=0.2)
         # global date_to_incidence_rate_by_phu

### 2022-12-23 Model/ModelData.py

@@ -125,9 +125,32 @@ class ModelData:
         This is hard and trciky!
         :return:
         """
+
         dose1 = np.clip((self.time_series_vaccinated[0] - self.time_series_vaccinated[1])[:date], a_min=0, a_max=1)
         dose2 = np.clip((self.time_series_vaccinated[1] - self.time_series_vaccinated[2])[:date], a_min=0, a_max=1)
         dose3 = (self.time_series_vaccinated[2])[:date]
+
+        print(np.sum(self.time_series_vaccinated[0], axis=0))
+        print(np.sum(self.time_series_vaccinated[1], axis=0))
+        print(np.sum(self.time_series_vaccinated[2], axis=0))
+
+        print('WHY?')
+
+        print(np.sum(self.time_series_vaccinated[0]))
+        print(np.sum(self.time_series_vaccinated[1]))
+        print(np.sum(self.time_series_vaccinated[2]))
+
+        print('FUCK?')
+
+        print(np.sum(dose1))
+        print(np.sum(dose2))
+        print(np.sum(dose3))
+
+        """
+        print(np.sum(dose1, axis=0))
+        print(np.sum(dose2, axis=0))
+        print(np.sum(dose3, axis=0))
+        """
 
         dose1 = (np.ones(shape=(Parameters.NO_COUNTY, dose1.shape[0], dose1.shape[1])) * dose1).transpose(1, 0, 2)
         dose2 = (np.ones(shape=(Parameters.NO_COUNTY, dose2.shape[0], dose2.shape[1])) * dose2).transpose(1, 0, 2)
@@ -182,14 +205,18 @@ class ModelData:
         print(np.max(immunity_dose1))
         print(np.max(immunity_dose2))
 
-        immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 + immunity_infection
+        vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3
+
+        immunity = vaccine_immunity + immunity_infection
 
         print(immunity.shape)
 
         today_immunity = np.sum(immunity, axis=0)
+        today_vaccine_immunity = np.sum(vaccine_immunity, axis=0)
 
         print(today_immunity.shape)
         print(np.max(today_immunity))
+        print(np.max(today_vaccine_immunity))
 
 
 

### 2022-12-23 Model/Dependency.py
bugs to be fixed.

@@ -302,9 +302,8 @@ class Dependency:
 
         """
 
-        dose1 = np.clip((self.date_to_vaccines_by_age[0] - self.date_to_vaccines_by_age[1]), a_min=0, a_max=1)
-        dose2 = np.clip((self.date_to_vaccines_by_age[1] - self.date_to_vaccines_by_age[2]), a_min=0, a_max=1)
-        dose3 = (self.date_to_vaccines_by_age[2])
+        print(self.date_to_vaccines_by_age.shape)
+
 
         for i in range(self.total_days - 1):
 
@@ -312,8 +311,6 @@ class Dependency:
 
             vaccine_differentiated[i+1] = self.date_to_vaccines_by_age[i+1] - self.date_to_vaccines_by_age[i]
         self.date_to_vaccines_by_age = np.clip(vaccine_differentiated, a_min=0, a_max=0.2)
-        # global date_to_incidence_rate_by_phu
-
         """
                 cases_differentiated = dict()
         for phu in self.date_to_incidence_rate_by_phu:
@@ -327,6 +324,20 @@ class Dependency:
 
         self.date_to_incidence_rate_by_phu = cases_differentiated
         """
+
+        data = self.date_to_vaccines_by_age.transpose(1, 0, 2)
+
+        dose1 = np.clip((data[0] - data[1]), a_min=0, a_max=1)
+        dose2 = np.clip((data[1] - data[2]), a_min=0, a_max=1)
+        dose3 = (data[2])
+
+        # print('WHYYYYYY?')
+
+        # print(np.max(dose1))
+        # print(np.max(dose2))
+        # print(np.max(dose3))
+
+        # self.date_to_vaccines_by_age = np.array([dose1, dose2, dose3]).transpose(1, 0, 2)
 
         return
 

### 2022-12-23 Model/ModelData.py

@@ -105,7 +105,7 @@ class ModelData:
         self.time_series_hospitalized = np.concatenate([self.dependency.date_to_hospitalizations_by_county,
                                                         np.zeros(shape=(x, y, z))], axis=1)
 
-        self.time_series_ICU =  np.concatenate([self.dependency.date_to_hospitalizations_by_county,
+        self.time_series_ICU = np.concatenate([self.dependency.date_to_hospitalizations_by_county,
                                                         np.zeros(shape=(x, y, z))], axis=1)
 
         self.time_series_vaccinated = np.concatenate([self.dependency.date_to_vaccines_by_age,
@@ -126,8 +126,8 @@ class ModelData:
         :return:
         """
 
-        dose1 = np.clip((self.time_series_vaccinated[0] - self.time_series_vaccinated[1])[:date], a_min=0, a_max=1)
-        dose2 = np.clip((self.time_series_vaccinated[1] - self.time_series_vaccinated[2])[:date], a_min=0, a_max=1)
+        dose1 = (self.time_series_vaccinated[0])[:date]
+        dose2 = (self.time_series_vaccinated[1])[:date]
         dose3 = (self.time_series_vaccinated[2])[:date]
 
         print(np.sum(self.time_series_vaccinated[0], axis=0))
@@ -196,8 +196,16 @@ class ModelData:
         print(kernel_dose_1.shape)
 
         immunity_dose1 = np.multiply(dose1, kernel_dose_1)
+
+        immunity_dose2_rmv = np.multiply(dose2, kernel_dose_1)
+
         immunity_dose2 = np.multiply(dose2, kernel_dose_2)
+
         immunity_dose3 = np.multiply(dose3, kernel_dose_3)
+
+        immunity_dose3_rmv = np.multiply(dose3, kernel_dose_2)
+
+
         immunity_infection = np.multiply(today_incidence, kernel_infection)
 
         print('HOLY!')
@@ -205,11 +213,14 @@ class ModelData:
         print(np.max(immunity_dose1))
         print(np.max(immunity_dose2))
 
-        vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3
+        vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose3_rmv - immunity_dose2_rmv
 
-        immunity = vaccine_immunity + immunity_infection
+        immunity = vaccine_immunity + (1 - vaccine_immunity) * immunity_infection
 
[…]

### 2022-12-23 Model/ModelData.py
哈哈哈哈bug修完了哈哈哈哈哈好开心哈哈哈

@@ -70,9 +70,9 @@ class ModelData:
             """
                 Note that!!! We asssumed an consistent vaccination level acrross ALL counties in ON!
             """
-            self.time_series_vaccinated = np.zeros(shape=(y, z), dtype=int)
+            self.time_series_vaccinated = np.zeros(shape=(x, y, z), dtype=int)
 
-            self.time_series_immunity = np.zeros(shape=(x, self.time_series_len, z), dtype=float)
+            self.time_series_immunity = np.zeros(shape=(x, y, z), dtype=float)
 
     def _load_from_dependencies(self):
         x = len(self.dependency.county_data)
@@ -113,9 +113,10 @@ class ModelData:
 
         self.time_series_vaccinated = self.time_series_vaccinated.transpose(1, 0, 2)
 
-
-        self.time_series_immunized = np.zeros(shape=(x, y, z), dtype=float)
-        self.time_series_immunity = np.zeros(shape=(x, y, z), dtype=float)
+        self.time_series_immunized = np.zeros(shape=(x, self.dependency.date_to_deaths_by_county.shape[1] + y,
+                                                     z), dtype=float)
+        self.time_series_immunity = np.zeros(shape=(x, self.dependency.date_to_deaths_by_county.shape[1] + y,
+                                                    z), dtype=float)
 
     def compute_immunity(self, date):
         """
@@ -129,22 +130,6 @@ class ModelData:
         dose1 = (self.time_series_vaccinated[0])[:date]
         dose2 = (self.time_series_vaccinated[1])[:date]
         dose3 = (self.time_series_vaccinated[2])[:date]
-
-        print(np.sum(self.time_series_vaccinated[0], axis=0))
-        print(np.sum(self.time_series_vaccinated[1], axis=0))
-        print(np.sum(self.time_series_vaccinated[2], axis=0))
-
-        print('WHY?')
-
-        print(np.sum(self.time_series_vaccinated[0]))
-        print(np.sum(self.time_series_vaccinated[1]))
-        print(np.sum(self.time_series_vaccinated[2]))
-
-        print('FUCK?')
-
-        print(np.sum(dose1))
-        print(np.sum(dose2))
-        print(np.sum(dose3))
 
         """
         print(np.sum(dose1, axis=0))
@@ -165,13 +150,9 @@ class ModelData:
 
         ratio = age_population / np.sum(age_population)
 
-        print(county_population.shape)
-
[…]

### 2022-12-23 Model/Dependency.py
Debuged!

@@ -302,8 +302,6 @@ class Dependency:
 
         """
 
-        print(self.date_to_vaccines_by_age.shape)
-
 
         for i in range(self.total_days - 1):
 
@@ -330,14 +328,6 @@ class Dependency:
         dose1 = np.clip((data[0] - data[1]), a_min=0, a_max=1)
         dose2 = np.clip((data[1] - data[2]), a_min=0, a_max=1)
         dose3 = (data[2])
-
-        # print('WHYYYYYY?')
-
-        # print(np.max(dose1))
-        # print(np.max(dose2))
-        # print(np.max(dose3))
-
-        # self.date_to_vaccines_by_age = np.array([dose1, dose2, dose3]).transpose(1, 0, 2)
 
         return
 

### 2022-12-23 Model/Model.py

@@ -28,6 +28,7 @@ class Model:
         self._model_transition()
         today_cases = self._model_data.time_series_active_cases.transpose(1, 0, 2)
         print(np.sum(today_cases[self.date]))
+        # print(np.sum(self._model_data.time_series_immunity.transpose(1, 0, 2)[self.date]))
         return
 
     def _model_transition(self):

### 2022-12-23 Model/ModelData.py

@@ -131,11 +131,7 @@ class ModelData:
         dose2 = (self.time_series_vaccinated[1])[:date]
         dose3 = (self.time_series_vaccinated[2])[:date]
 
-        """
-        print(np.sum(dose1, axis=0))
-        print(np.sum(dose2, axis=0))
-        print(np.sum(dose3, axis=0))
-        """
+
 
         dose1 = (np.ones(shape=(Parameters.NO_COUNTY, dose1.shape[0], dose1.shape[1])) * dose1).transpose(1, 0, 2)
         dose2 = (np.ones(shape=(Parameters.NO_COUNTY, dose2.shape[0], dose2.shape[1])) * dose2).transpose(1, 0, 2)
@@ -174,7 +170,6 @@ class ModelData:
         kernel_dose_3 = np.multiply(raw_kernel_dose_3[:date].reshape(date, 1, 1), ratio)
         kernel_infection = np.multiply(raw_kernel_infection[:date].reshape(date, 1, 1), ratio)
 
-        print(kernel_dose_1.shape)
 
         immunity_dose1 = np.multiply(dose1, kernel_dose_1)
 

### 2022-12-23 Model/Model.py
Update

@@ -24,12 +24,84 @@ class Model:
         """
         self.date += 1
         print(self.date)
-        self._model_data.compute_immunity(self.date)
+        self._compute_immunity(self.date)
         self._model_transition()
         today_cases = self._model_data.time_series_active_cases.transpose(1, 0, 2)
         print(np.sum(today_cases[self.date]))
         # print(np.sum(self._model_data.time_series_immunity.transpose(1, 0, 2)[self.date]))
         return
+
+
+    def _compute_immunity(self, date):
+        """
+        For EXTERNAL call only
+        TODO: Find the vaccine efficacy and immunity waning function from papers, and
+        TODO: calcualte the immunity from the vaccination and cases data
+        This is hard and trciky!
+        :return:
+        """
+
+        dose1 = (self._model_data.time_series_vaccinated[0])[:date]
+        dose2 = (self._model_data.time_series_vaccinated[1])[:date]
+        dose3 = (self._model_data.time_series_vaccinated[2])[:date]
+
+
+
+        dose1 = (np.ones(shape=(Parameters.NO_COUNTY, dose1.shape[0], dose1.shape[1])) * dose1).transpose(1, 0, 2)
+        dose2 = (np.ones(shape=(Parameters.NO_COUNTY, dose2.shape[0], dose2.shape[1])) * dose2).transpose(1, 0, 2)
+        dose3 = (np.ones(shape=(Parameters.NO_COUNTY, dose3.shape[0], dose3.shape[1])) * dose3).transpose(1, 0, 2)
+
+
+        county_population = np.array(self.dependency.index_to_population)
+        county_population = county_population.reshape(county_population.shape[0], 1)
+
+        age_population = self.dependency.population_by_age_band
+        age_population = age_population.reshape(age_population.shape[0], 1)
+
+        ratio = age_population / np.sum(age_population)
+
+        population = np.matmul(county_population, ratio.T)
+
+        today_population = np.ones(shape=(date, population.shape[0], population.shape[1])) * population
+
+        today_cases = self._model_data.time_series_infected.transpose(1, 0, 2)[:date]
+
+        today_incidence = today_cases / today_population
+
[…]

### 2022-12-23 Model/ModelData.py

@@ -118,124 +118,4 @@ class ModelData:
         self.time_series_immunity = np.zeros(shape=(x, self.dependency.date_to_deaths_by_county.shape[1] + y,
                                                     z), dtype=float)
 
-    def compute_immunity(self, date):
-        """
-        For EXTERNAL call only
-        TODO: Find the vaccine efficacy and immunity waning function from papers, and
-        TODO: calcualte the immunity from the vaccination and cases data
-        This is hard and trciky!
-        :return:
-        """
-
-        dose1 = (self.time_series_vaccinated[0])[:date]
-        dose2 = (self.time_series_vaccinated[1])[:date]
-        dose3 = (self.time_series_vaccinated[2])[:date]
-
-
-
-        dose1 = (np.ones(shape=(Parameters.NO_COUNTY, dose1.shape[0], dose1.shape[1])) * dose1).transpose(1, 0, 2)
-        dose2 = (np.ones(shape=(Parameters.NO_COUNTY, dose2.shape[0], dose2.shape[1])) * dose2).transpose(1, 0, 2)
-        dose3 = (np.ones(shape=(Parameters.NO_COUNTY, dose3.shape[0], dose3.shape[1])) * dose3).transpose(1, 0, 2)
-
-
-        county_population = np.array(self.dependency.index_to_population)
-        county_population = county_population.reshape(county_population.shape[0], 1)
-
-        age_population = self.dependency.population_by_age_band
-        age_population = age_population.reshape(age_population.shape[0], 1)
-
-        ratio = age_population / np.sum(age_population)
-
-        population = np.matmul(county_population, ratio.T)
-
-        today_population = np.ones(shape=(date, population.shape[0], population.shape[1])) * population
-
-        today_cases = self.time_series_infected.transpose(1, 0, 2)[:date]
-
-        today_incidence = today_cases / today_population
-
-        self.time_series_incidence = today_incidence.transpose(1, 0, 2)
-
-        # TODO: convolution on these three categories each with type (x, 16), respectively, and add up.
-
-
-        raw_kernel_dose_1 = Parameters.VACCINE_EFFICACY_KERNEL_DOSE1[::-1]
-        raw_kernel_dose_2 = Parameters.VACCINE_EFFICACY_KERNEL_DOSE2[::-1]
[…]

### 2022-12-23 Model/Model.py
Update Model.py

@@ -34,23 +34,16 @@ class Model:
 
     def _compute_immunity(self, date):
         """
-        For EXTERNAL call only
-        TODO: Find the vaccine efficacy and immunity waning function from papers, and
-        TODO: calcualte the immunity from the vaccination and cases data
-        This is hard and trciky!
-        :return:
+        TODO: Find the vaccine efficacy and immunity waning function from papers
         """
 
         dose1 = (self._model_data.time_series_vaccinated[0])[:date]
         dose2 = (self._model_data.time_series_vaccinated[1])[:date]
         dose3 = (self._model_data.time_series_vaccinated[2])[:date]
 
-
-
         dose1 = (np.ones(shape=(Parameters.NO_COUNTY, dose1.shape[0], dose1.shape[1])) * dose1).transpose(1, 0, 2)
         dose2 = (np.ones(shape=(Parameters.NO_COUNTY, dose2.shape[0], dose2.shape[1])) * dose2).transpose(1, 0, 2)
         dose3 = (np.ones(shape=(Parameters.NO_COUNTY, dose3.shape[0], dose3.shape[1])) * dose3).transpose(1, 0, 2)
-
 
         county_population = np.array(self.dependency.index_to_population)
         county_population = county_population.reshape(county_population.shape[0], 1)
@@ -81,16 +74,13 @@ class Model:
         kernel_dose_3 = np.multiply(raw_kernel_dose_3[:date].reshape(date, 1, 1), ratio)
         kernel_infection = np.multiply(raw_kernel_infection[:date].reshape(date, 1, 1), ratio)
 
-
         immunity_dose1 = np.multiply(dose1, kernel_dose_1)
         immunity_dose2_rmv = np.multiply(dose2, kernel_dose_1)
         immunity_dose2 = np.multiply(dose2, kernel_dose_2)
         immunity_dose3 = np.multiply(dose3, kernel_dose_3)
         immunity_dose3_rmv = np.multiply(dose3, kernel_dose_2)
 
-
         infection_immunity = np.multiply(today_incidence, kernel_infection)
-
         vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose3_rmv - immunity_dose2_rmv
         today_infection_immunity = np.sum(infection_immunity, axis=0)
         today_vaccine_immunity = np.sum(vaccine_immunity, axis=0)

### 2022-12-23 Model/Model.py
Update model

@@ -1,5 +1,9 @@
 import math
+import os
+
 import numpy as np
+import pandas as pd
+
 import Dependency as Dependency
 from ModelData import ModelData
 import Parameters
@@ -10,6 +14,9 @@ class Model:
     _model_data = None
 
     date = 0
+
+    day_outflow = None
+    day_inflow = None
 
     def __init__(self, forecast_days=1000):
         self._initialize_dependencies()
@@ -25,12 +32,15 @@ class Model:
         self.date += 1
         print(self.date)
         self._compute_immunity(self.date)
-        self._model_transition()
+        self._model_transition(time_step='day')
+
+        self._compute_immunity(self.date)
+        self._model_transition(time_step='night')
+
         today_cases = self._model_data.time_series_active_cases.transpose(1, 0, 2)
         print(np.sum(today_cases[self.date]))
         # print(np.sum(self._model_data.time_series_immunity.transpose(1, 0, 2)[self.date]))
         return
-
 
     def _compute_immunity(self, date):
         """
@@ -85,7 +95,7 @@ class Model:
         today_infection_immunity = np.sum(infection_immunity, axis=0)
         today_vaccine_immunity = np.sum(vaccine_immunity, axis=0)
 
-        today_immunity = today_vaccine_immunity + (np.ones(shape=(Parameters.NO_COUNTY, 16)) - today_vaccine_immunity)\
+        today_immunity = today_vaccine_immunity + (np.ones(shape=(Parameters.NO_COUNTY, 16)) - today_vaccine_immunity) \
                          * today_infection_immunity
 
         data = self._model_data.time_series_immunity.transpose(1, 0, 2)
@@ -93,12 +103,13 @@ class Model:
         self._model_data.time_series_immunity = data.transpose(1, 0, 2)
         return None
 
-    def _model_transition(self):
-        self._susceptible_to_exposed(self.date)
-        self._exposed_to_cases(self.date)
-        self._infected_to_hospitalized(self.date)
-        self._hospitalized_to_icu(self.date)
-        self._infected_to_removed(self.date)
+    def _model_transition(self, time_step='day'):
+        self._susceptible_to_exposed(self.date, time_step=time_step)
+        if time_step == 'night':
+            self._exposed_to_cases(self.date)
+            self._infected_to_hospitalized(self.date)
+            self._hospitalized_to_icu(self.date)
+            self._infected_to_removed(self.date)
 
[…]

### 2022-12-23 Model/ModelData.py

@@ -83,7 +83,7 @@ class ModelData:
                                                           np.zeros(shape=(x, y, z))], axis=1)
 
         self.time_series_active_cases = np.multiply(self.time_series_clinical_cases,
-                                                    Parameters.BAYES_CLINICAL_BY_AGE.T)
+                                                    Parameters.REVERSE_CLINICAL_BY_AGE.T)
 
         self.time_series_exposed = copy.deepcopy(self.time_series_active_cases)
 

### 2022-12-23 Model/Parameters.py

@@ -14,25 +14,12 @@ import datetime
 ver = '1.0'
 
 
-def find_mean(v):
-    tot = 0
-    for i in range(len(v)):
-        tot += v[i]
-        if tot >= 0.5:
-            print(i, len(v))
-            break
-
-
-def get_bayes(lst):
-    bayes = np.zeros(shape=lst.shape)
-    for i in range(lst.shape[0]):
-        bayes[i] = 1 / lst[i]
-    return bayes
-
-
 def get_immunity_kernel(dose=0, length=2000):
     kernel = np.ones(shape=(length,), dtype=float)
     return kernel
+
+
+INFECTIOUSNESS = 0.08
 
 
 """
@@ -101,7 +88,7 @@ SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - CLINICAL_RATIO
     Bayes
 """
 
-BAYES_CLINICAL_BY_AGE = get_bayes(CLINICAL_RATIO)
+REVERSE_CLINICAL_BY_AGE = np.ones(shape=CLINICAL_RATIO.shape) / CLINICAL_RATIO
 
 # Work force
 LABOUR_FORCE_BY_AGE = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 0.106146399, 0.106351741,
@@ -113,6 +100,11 @@ LABOUR_FORCE_BY_AGE = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 0.1
 """
 VACCINE_AGE_BANDS = ['05-11yrs', '12-17yrs', '18-29yrs', '30-39yrs', '40-49yrs', '50-59yrs', '60-69yrs', '70-79yrs',
                      '80+']
+
+
+AGE_BANDS = ['0-4yrs', '5-9yrs', '10-14yrs', '15-19yrs', '20-24yrs', '25-29yrs', '30-34yrs', '35-39yrs', '40-44yrs',
+             '45-49yrs', '50-54yrs', '55-59yrs', '60-64yrs', '65-69yrs', '70-74yrs', '75+yrs']
+
 
 """
     Convolution kernels

### 2022-12-25 Model/Dependency.py
Update code, now trying to fit the model.

@@ -195,7 +195,7 @@ class Dependency:
             elements = lines[line]
             elements[1] = elements[1].replace('"', '')
             string = elements[0]
-            this_day = datetime.strptime(string, '%d-%b-%y')
+            this_day = datetime.strptime(string, '%B %d, %Y')
             after_outbreak = (this_day - Parameters.OUTBREAK_FIRST_DAY).days
             phu = elements[1]
             if after_outbreak > last_recorded:
@@ -225,42 +225,33 @@ class Dependency:
         return
 
     def read_vaccine(self):
-        read_path = self.get_dependency_path() + 'vaccines_by_age.csv'
-        with open(read_path) as file:
-            contents = file.read()
-        lines = contents.split('\n')
+        read_path = self.get_dependency_path() + 'vaccine_by_age_auto_update.csv'
+        vaccine_df = pd.read_csv(read_path)
+
+        vaccine_df['Percent_at_least_one_dose'] = vaccine_df['Percent_at_least_one_dose'].fillna(0)
+        vaccine_df['Percent_fully_vaccinated'] = vaccine_df['Percent_fully_vaccinated'].fillna(0)
+        vaccine_df['Percent_3doses'] = vaccine_df['Percent_3doses'].fillna(0)
+
+        vaccine_df['Date'] = pd.to_datetime(vaccine_df['Date'])
 
         self.find_max_date()
 
-        # global date_to_vaccines_by_age
         self.date_to_vaccines_by_age = np.zeros((self.total_days, 3, 9))
-        for line in range(1, len(lines) - 1):
-            elements = lines[line].split(',')
-            string = elements[0]
-            this_day = datetime.strptime(string, '%m/%d/%Y')
-            after_outbreak = (this_day - Parameters.OUTBREAK_FIRST_DAY).days
-            band = elements[1]
 
-            for i in [7, 8, 9]:
-                if elements[i] == '':
-                    elements[i] = 0
+        for i in range(len(vaccine_df)):
+            row = vaccine_df.iloc[i]
+            after_outbreak = (row['Date'] - Parameters.OUTBREAK_FIRST_DAY).days
+            band = row['Agegroup']
 
             if band in Parameters.VACCINE_AGE_BANDS:
-                for i in [7, 8, 9]:
-                    if elements[i] == '':
-                        elements[i] = 0
                 self.date_to_vaccines_by_age[after_outbreak - 1][0][Parameters.VACCINE_AGE_BANDS.index(band)] = float(
[…]

### 2022-12-25 Model/Gaussian.py

@@ -1,67 +1,38 @@
 import math
 import Parameters
+import numpy as np
+import cv2
 
-
-def difference_of_gaussian(lst):
+def blur(lst):
     """
         Perform difference of Gaussian ()
         :param lst:
         :return:
     """
-    sigma_1 = 10
-    sigma_2 = 30
-    age_bands = [5, 12, 18, 30, 40, 50, 60, 70, 80, 90]
-    cont_dist = [0] * 90
-    discr_dist = [0] * Parameters.MATRIX_SIZE
-    for age in range(90):
-        cuml = 0
-        for mu in range(len(age_bands)-1):
-            val = lst[mu]
-            mean = (age_bands[mu] + age_bands[mu+1]) / 2.0
-            diff = age - mean
-            beta = 1.0
-            sqrtpi = math.sqrt(math.pi)
-            add = (beta * math.e ** (- (diff ** 2.0) / (2.0 * (sigma_1 ** 2.0)))) / (sigma_1 * sqrtpi) * val
-            minus = - (beta * math.e ** (- (diff ** 2.0) / (2.0 * (sigma_2 ** 2.0)))) / (sigma_2 * sqrtpi) * val
-            minus = 0
-            cuml += (add + minus)
-        cont_dist[age] = cuml
+    raw = np.zeros(shape=(100, ))
+    raw[5:12] = lst[0]
+    raw[12:18] = lst[1]
+    raw[18:30] = lst[2]
+    raw[30:40] = lst[3]
+    raw[40:50] = lst[4]
+    raw[50:60] = lst[5]
+    raw[60:70] = lst[6]
+    raw[70:80] = lst[7]
+    raw[80:] = lst[8]
 
-    for age in range(90):
-        cont_dist[age] = cont_dist[age] * 6.7
+    blurred = np.reshape(np.array(cv2.GaussianBlur(raw.reshape(100, 1), (9, 9), 0)), newshape=(100,))
 
-    matrix_16_bands = [0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 90]
-    for i in range(Parameters.MATRIX_SIZE):
-        discr_dist[i] = integrate(cont_dist, matrix_16_bands[i], matrix_16_bands[i+1])
+    rslt = np.zeros(shape=(16, ))
 
-    # Compensation for the last entry for not having a right approximation
-    discr_dist[15] *= 1.24
[…]

### 2022-12-25 Model/Model.py

@@ -21,11 +21,14 @@ class Model:
 
     infectiousness = 0
 
-    def __init__(self, forecast_days=1000, infectiousness=Parameters.INFECTIOUSNESS, prior_immunity=0):
+    model_fitting = False
+
+    def __init__(self, forecast_days=1000, infectiousness=Parameters.INFECTIOUSNESS, prior_immunity=0, fitting=False):
         self._initialize_dependencies()
         self._model_data = ModelData(forecast_days, self.dependency, load_from_dependency=True, prior_immunity=prior_immunity)
         self.date = self.dependency.total_days - 1
         self.infectiousness = infectiousness
+        self.model_fitting = fitting
         return
 
     def run_one_cycle(self, display_status=False):
@@ -39,13 +42,16 @@ class Model:
         self._compute_immunity(self.date)
         self._model_transition(time_step='night')
 
-        today_cases = self._model_data.time_series_active_cases.transpose(1, 0, 2)
         if display_status:
-            print(self.date)
-            print('Today_new_cases', np.sum(today_cases[self.date]))
-            print('Total new cases', np.sum(self._model_data.time_series_active_cases))
-        # print(np.sum(self._model_data.time_series_immunity.transpose(1, 0, 2)[self.date]))
+            self.print_data(self.date)
         return
+
+    def print_data(self, date):
+        print(date)
+        today_cases = self._model_data.time_series_active_cases.transpose(1, 0, 2)
+        print('Today_new_cases', np.sum(today_cases[date]))
+        print('Total cases', np.sum(self._model_data.time_series_active_cases))
+        print('Immunity', np.max(self._model_data.time_series_immunity.transpose(1, 0, 2)[date][0]))
 
     def _compute_immunity(self, date):
         """
@@ -70,11 +76,11 @@ class Model:
 
         population = np.matmul(county_population, ratio.T)
 
-        today_population = np.ones(shape=(date, population.shape[0], population.shape[1])) * population
+        today_population = np.ones(shape=(population.shape[0], population.shape[1])) * population
 
         today_cases = self._model_data.time_series_infected.transpose(1, 0, 2)[:date]
 
-        today_incidence = today_cases / today_population
[…]

### 2022-12-25 Model/ModelData.py

@@ -90,7 +90,7 @@ class ModelData:
 
         self.time_series_sub_clinical_cases = self.time_series_active_cases - self.time_series_clinical_cases
 
-        # TODO: update this
+        # Note: these values are obtained from convolution.
 
         self.time_series_recovered = np.apply_along_axis(lambda m:
                                                          np.convolve(m,
@@ -107,10 +107,12 @@ class ModelData:
         self.time_series_ICU = np.concatenate([self.dependency.date_to_ICU_by_county,
                                                         np.zeros(shape=(x, y, z))], axis=1)
 
-        # NOTE: here we assumed constant vaccination!!!!
+        # NOTE: Vaccination assumtpions, might need to change here.
+
+        vaccine_adjust = np.concatenate([np.zeros(shape=(y, 2, z)), 0.015 * np.ones(shape=(y, 1, z))], axis=1)
 
         self.time_series_vaccinated = np.concatenate([self.dependency.date_to_vaccines_by_age,
-                                                      0.002 * np.ones(shape=(y, 3, z))], axis=0)
+                                                      vaccine_adjust], axis=0)
 
         self.time_series_vaccinated = self.time_series_vaccinated.transpose(1, 0, 2)
 
@@ -199,14 +201,11 @@ class ModelData:
             kernel_infection = np.multiply(raw_kernel_infection.reshape(date, 1, 16), ratio)
 
             immunity_dose1 = np.multiply(dose1, kernel_dose_1)
-            immunity_dose2_rmv = np.multiply(dose2, kernel_dose_1)
             immunity_dose2 = np.multiply(dose2, kernel_dose_2)
             immunity_dose3 = np.multiply(dose3, kernel_dose_3)
-            immunity_dose3_rmv = np.multiply(dose3, kernel_dose_2)
 
             infection_immunity = np.multiply(today_incidence, kernel_infection)
-            vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose3_rmv -\
-                               immunity_dose2_rmv
+            vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3
 
             vaccine_immunity[:][:][0] = 0
 

### 2022-12-25 Model/Parameters.py

@@ -19,7 +19,8 @@ ver = '1.0'
 def get_immunity_kernel(dose=0, length=2000):
     if dose == 0:
         # TODO: natural immunity this is incorrect, update!
-        return THREE_DOSE_EFFICACY
+        return np.ones(shape=TWO_DOSE_EFFICACY.shape) - 0.15 * \
+            (np.ones(shape=TWO_DOSE_EFFICACY.shape)  - TWO_DOSE_EFFICACY)
     elif dose == 1:
         return 0.8 * TWO_DOSE_EFFICACY
     elif dose == 2:
@@ -36,7 +37,7 @@ DEPENDENCY_PATH = os.getcwd()[:-5] + 'Model Dependencies/'
 TWO_DOSE_EFFICACY = df = pd.read_csv(DEPENDENCY_PATH + 'two_dose.csv', delimiter=',').to_numpy().T[1:17].T
 THREE_DOSE_EFFICACY = df = pd.read_csv(DEPENDENCY_PATH + 'three_dose.csv', delimiter=',').to_numpy().T[1:17].T
 
-INFECTIOUSNESS = 0.03
+INFECTIOUSNESS = 0.08
 
 """
     Matrix constants
@@ -67,6 +68,12 @@ OUTBREAK_FIRST_DAY = datetime.datetime(2020, 1, 15)
 """
     Ontario age-specific parameters Done!
 """
+
+ONT_POPULATOIN = 15109416
+
+ONT_AGE_BAND_POPULATION = np.array([714654, 769062, 803899, 849806, 1057366, 1125877, 1103728, 1042232, 953628,
+                                    920118, 952509, 1037514, 1004860, 855432, 702717, 1216014])
+
 
 ICU_HOSP = 0.1540844459589232
 
@@ -110,7 +117,7 @@ SUSC_RATIO = np.array([3.991327254652800027e-01, 3.948075309394725174e-01, 4.022
 
 CLINICAL_RATIO = np.array([0.2865309, 0.26753682, 0.23495708, 0.23019938, 0.25561971, 0.28454104,
                            0.31587461, 0.34737841, 0.38386853, 0.42265894, 0.47025061, 0.52584302,
-                           0.59291004, 0.64122657, 0.67295434, 0.71677774])
+                           0.59291004, 0.64122657, 0.67295434, 0.71677774]) * 1
 
[…]

### 2022-12-25 Model/Update.py

@@ -1,0 +1,18 @@
+import pandas as pd
+import requests
+import os
+
+vaccine_url = 'https://data.ontario.ca/dataset/752ce2b7-c15a-4965-a3dc-397bf405e7cc/resource/775ca815-5028-4e9b-9dd4' \
+      '-6975ff1be021/download/vaccines_by_age.csv'
+vaccine_request = requests.get(vaccine_url)
+path = os.getcwd()[:-5] + 'Model Dependencies/'
+
+open(path + 'vaccine_by_age_auto_update.csv', "wb").write(vaccine_request.content)
+
+
+admin_vaccine_url = 'https://data.ontario.ca/dataset/752ce2b7-c15a-4965-a3dc-397bf405e7cc/resource/8a89caa9-511c-' \
+                    '4568-af89-7f2174b4378c/download/vaccine_doses.csv'
+admin_vaccine_request = requests.get(admin_vaccine_url)
+path = os.getcwd()[:-5] + 'Model Dependencies/'
+
+open(path + 'vaccine_by_age_admin.csv', "wb").write(admin_vaccine_request.content)

### 2022-12-25 Model/Dependency.py
too lazy to write

@@ -59,6 +59,10 @@ class Dependency:
     population_by_age_band = np.zeros(shape=(16,), dtype=int)
     ratio_by_age_band = np.zeros(shape=(16,), dtype=int)
 
+    raw_mobility = None
+
+    mobility = None
+
     ontario_population = 0
 
     def __init__(self):
@@ -88,6 +92,79 @@ class Dependency:
         self.compute_phu_population()
         self.distribute_to_counties()
         self.read_age()
+        self.read_mobility()
+        self.mobility_reshape()
+
+
+    def read_mobility(self):
+        path = self.get_dependency_path()
+        read_path = path + 'Region_Mobility_Report_CSVs/'
+        path_2020 = read_path + '2020_CA_Region_Mobility_Report.csv'
+        path_2021 = read_path + '2021_CA_Region_Mobility_Report.csv'
+        path_2022 = read_path + '2022_CA_Region_Mobility_Report.csv'
+        df1 = pd.read_csv(path_2020)
+        df2 = pd.read_csv(path_2021)
+        df3 = pd.read_csv(path_2022)
+
+        df = pd.concat([df1, df2, df3])
+
+        df['date'] = pd.to_datetime(df['date'])
+
+        groups = df.groupby('iso_3166_2_code')
+        Ontario = groups.get_group('CA-ON')
+        max_date = (Ontario['date'].max() - Parameters.OUTBREAK_FIRST_DAY).days
+        min_date = (Ontario['date'].min() - Parameters.OUTBREAK_FIRST_DAY).days
+
+        mobility = np.zeros(shape=(6, 3000))
+
+        retail = Ontario['retail_and_recreation_percent_change_from_baseline'].to_numpy()
+        grocery = Ontario['grocery_and_pharmacy_percent_change_from_baseline'].to_numpy()
+        park = Ontario['parks_percent_change_from_baseline'].to_numpy()
+        trainsit = Ontario['transit_stations_percent_change_from_baseline'].to_numpy()
+        workplace = Ontario['workplaces_percent_change_from_baseline'].to_numpy()
+        residential = Ontario['residential_percent_change_from_baseline'].to_numpy()
+        mobility[0][min_date:max_date + 1] = retail
+        mobility[1][min_date:max_date + 1] = grocery
+        mobility[2][min_date:max_date + 1] = park
+        mobility[3][min_date:max_date + 1] = trainsit
+        mobility[4][min_date:max_date + 1] = workplace
+        mobility[5][min_date:max_date + 1] = residential
[…]

### 2022-12-25 Model/Model.py

@@ -44,6 +44,7 @@ class Model:
 
         if display_status:
             self.print_data(self.date)
+            print(self.dependency.mobility[self.date])
         return
 
     def print_data(self, date):
@@ -106,7 +107,8 @@ class Model:
 
         infection_immunized = np.sum(np.multiply(today_incidence, kernel_infection), axis=0)
 
-        vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose1_rmv - immunity_dose2_rmv
+        # vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose1_rmv - immunity_dose2_rmv
+        vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose2_rmv
 
         infection_immunity = infection_immunized / today_population
         vaccine_immunized = vaccine_immunity * today_population
@@ -128,6 +130,8 @@ class Model:
         # print(vaccine_immunity[0])
         # print(infection_immunity[0])
         # print(today_immunity[0])
+
+        # TODO: DEBUG THIS
 
         data = self._model_data.time_series_immunity.transpose(1, 0, 2)
         data[date] = today_immunity
@@ -168,7 +172,15 @@ class Model:
 
             tot_infectiouesness = clinical_infectious + 0.5 * (sub_clinical_infectious + exposed_infectious)
 
-            rslt = self._get_new_cases(tot_infectiouesness, contact_type=0, contact_pattern=time_step) * immunity
+            county_data = self.dependency.county_data[c]
+
+            if county_data[2] > 10000:
+                type = 0
+            else:
+                type = 1
+
+
+            rslt = self._get_new_cases(tot_infectiouesness, contact_type=type, contact_pattern=time_step) * immunity
             # print(rslt)
             if time_step == 'day':
                 self._model_data.time_series_exposed[c][date] = rslt
@@ -301,7 +313,7 @@ class Model:
         preset = Parameters.MATRIX_PRESETS[contact_pattern]
         matrix = np.zeros(shape=(16, 16))
         for j in range(4):
-            matrix = np.add(matrix, preset[j] * matrices[contact_type][j])
+            matrix = np.add(matrix, preset[j] * matrices[contact_type][j]) * self.dependency.mobility[self.date][j]
         return matrix * self.infectiousness
 
     def _initialize_dependencies(self):

### 2022-12-25 Model/ModelData.py

@@ -109,7 +109,8 @@ class ModelData:
 
         # NOTE: Vaccination assumtpions, might need to change here.
 
-        vaccine_adjust = np.concatenate([np.zeros(shape=(y, 2, z)), 0.015 * np.ones(shape=(y, 1, z))], axis=1)
+        vaccine_adjust = np.concatenate([np.zeros(shape=(y, 2, z)), 0.001 * Parameters.ONT_VACCINE_DISTRIBUTION * 16
+                                         * np.ones(shape=(y, 1, 1))], axis=1)
 
         self.time_series_vaccinated = np.concatenate([self.dependency.date_to_vaccines_by_age,
                                                       vaccine_adjust], axis=0)

### 2022-12-25 Model/Parameters.py

@@ -69,6 +69,11 @@ OUTBREAK_FIRST_DAY = datetime.datetime(2020, 1, 15)
     Ontario age-specific parameters Done!
 """
 
+
+ONT_VACCINE_DISTRIBUTION = np.array([0.00060537, 0.00458526, 0.01328221, 0.02727299, 0.04668258, 0.0514049, 0.05772092,
+                                     0.05664295, 0.05666874, 0.05662532, 0.06529888, 0.07479382, 0.08567756, 0.07610751,
+                                     0.06813767, 0.25849333])
+
 ONT_POPULATOIN = 15109416
 
 ONT_AGE_BAND_POPULATION = np.array([714654, 769062, 803899, 849806, 1057366, 1125877, 1103728, 1042232, 953628,

### 2022-12-25 Model/Slice.py

@@ -1,5 +1,6 @@
 import csv
 import Dependency
+import os
 
 
 def group_by_county(county_name, data, index):
@@ -11,7 +12,7 @@ def group_by_county(county_name, data, index):
 
 
 def slice_ontario():
-    path = Dependency.get_dependency_path()
+    path = os.getcwd()[:-5] + 'Model Dependencies/'
     per_path = path + 'Region_Mobility_Report_CSVs/'
     years = ['2020', '2021', '2022']
     sur_path = '_CA_Region_Mobility_Report.csv'

### 2022-12-25 R code/Vaccine.R

@@ -1,0 +1,34 @@
+library('ggplot2')
+
+# NEED TO ADD CONFIDENCE INTERVAL!!!!
+
+
+df <- read.csv('D:/Github/Commuting_TSF_SARS-Cov-2_model_master/Analysis/Probabilistic_analysis/Raw_for_analysis/vaccine_paper_1.csv')
+
+p <- ggplot(df) + ylab('Attack rate') + xlab('Months upon immumnity gain') +
+  geom_point(aes(x = Month, y = Recovered_unvaccinated, color='blue')) + 
+  geom_line(aes(x = Month, y = Recovered_unvaccinated, color='blue')) +
+  geom_point(aes(x = Month, y = Two_dose, color='red')) +
+  geom_line(aes(x = Month, y = Two_dose, color='red')) +
+  scale_colour_discrete(name = "Cohort", labels = c("Natural immunity", "Vaccine immunity (2 dose)")) + 
+  facet_grid(. ~ Age_band) 
+
+p
+  
+ggsave("vaccine_unvaccinated.jpg", width = 10, height = 3)
+
+
+p <- ggplot(df) + ylab('Frequency') + xlab('Months upon immumnity gain') +
+  geom_point(aes(x = Month, y = Recovered_vaccinated, color='blue')) + 
+  geom_line(aes(x = Month, y = Recovered_vaccinated, color='blue')) +
+  geom_point(aes(x = Month, y = Vaccined_recovered, color='green')) + 
+  geom_line(aes(x = Month, y = Vaccined_recovered, color='green')) +
+  geom_point(aes(x = Month, y = Two_dose, color='red')) +
+  geom_line(aes(x = Month, y = Two_dose, color='red')) +
+  scale_colour_discrete(name = "Cohort", labels = c("Hybird immunity 1", "Hybird immunity 2", "Vaccine immunity (2 dose)")) + 
+  facet_grid(. ~ Age_band) 
+
+p
+
+ggsave("vaccine_vaccined.jpg", width = 10, height = 3)
+  

### 2022-12-25 R code/Vaccine.R
Update new files.

@@ -1,6 +1,5 @@
 library('ggplot2')
 
-# NEED TO ADD CONFIDENCE INTERVAL!!!!
 
 
 df <- read.csv('D:/Github/Commuting_TSF_SARS-Cov-2_model_master/Analysis/Probabilistic_analysis/Raw_for_analysis/vaccine_paper_1.csv')
@@ -16,7 +15,6 @@ p <- ggplot(df) + ylab('Attack rate') + xlab('Months upon immumnity gain') +
 p
   
 ggsave("vaccine_unvaccinated.jpg", width = 10, height = 3)
-
 
 p <- ggplot(df) + ylab('Frequency') + xlab('Months upon immumnity gain') +
   geom_point(aes(x = Month, y = Recovered_vaccinated, color='blue')) + 

### 2022-12-25 R code/Vaccine_paper_2.R

@@ -1,0 +1,32 @@
+library('ggplot2')
+
+
+
+df <- read.csv('D:/Github/Commuting_TSF_SARS-Cov-2_model_master/Analysis/Probabilistic_analysis/Raw_for_analysis/vaccine_paper_1.csv')
+
+p <- ggplot(df) + ylab('Attack rate') + xlab('Months upon immumnity gain') +
+  geom_point(aes(x = Month, y = Recovered_unvaccinated, color='blue')) + 
+  geom_line(aes(x = Month, y = Recovered_unvaccinated, color='blue')) +
+  geom_point(aes(x = Month, y = Two_dose, color='red')) +
+  geom_line(aes(x = Month, y = Two_dose, color='red')) +
+  scale_colour_discrete(name = "Cohort", labels = c("Natural immunity", "Vaccine immunity (2 dose)")) + 
+  facet_grid(. ~ Age_band) 
+
+p
+
+ggsave("vaccine_unvaccinated.jpg", width = 10, height = 3)
+
+
+p <- ggplot(df) + ylab('Frequency') + xlab('Months upon immumnity gain') +
+  geom_point(aes(x = Month, y = Recovered_vaccinated, color='blue')) + 
+  geom_line(aes(x = Month, y = Recovered_vaccinated, color='blue')) +
+  geom_point(aes(x = Month, y = Vaccined_recovered, color='green')) + 
+  geom_line(aes(x = Month, y = Vaccined_recovered, color='green')) +
+  geom_point(aes(x = Month, y = Two_dose, color='red')) +
+  geom_line(aes(x = Month, y = Two_dose, color='red')) +
+  scale_colour_discrete(name = "Cohort", labels = c("Hybird immunity 1", "Hybird immunity 2", "Vaccine immunity (2 dose)")) + 
+  facet_grid(. ~ Age_band) 
+
+p
+
+ggsave("vaccine_vaccined.jpg", width = 10, height = 3)

### 2022-12-26 Model/Dependency.py
Fitted the vaccine waning

@@ -1,5 +1,7 @@
 import copy
 from datetime import datetime
+
+import cv2
 import numpy as np
 import os
 import csv
@@ -136,13 +138,17 @@ class Dependency:
 
     def mobility_reshape(self):
         year_forecast = 10
-        no_shcool_day_start = datetime.strptime('2020-04-25', '%Y-%m-%d')
-        no_shcool_day_end = datetime.strptime('2020-09-04', '%Y-%m-%d')
+        summer_break_day_start = datetime.strptime('2020-04-25', '%Y-%m-%d')
+        summer_break_day_end = datetime.strptime('2020-09-04', '%Y-%m-%d')
 
-        no_school_start = (no_shcool_day_start - Parameters.OUTBREAK_FIRST_DAY).days
-        no_school_end = (no_shcool_day_end - Parameters.OUTBREAK_FIRST_DAY).days
+        winter_break_day_start = datetime.strptime('2020-12-20', '%Y-%m-%d')
+        winter_break_day_end = datetime.strptime('2021-01-09', '%Y-%m-%d')
 
-        # print(no_school_start, no_school_end)
+        summer_break_start = (summer_break_day_start - Parameters.OUTBREAK_FIRST_DAY).days
+        summer_break_end = (summer_break_day_end - Parameters.OUTBREAK_FIRST_DAY).days
+
+        christmas_start = (winter_break_day_start - Parameters.OUTBREAK_FIRST_DAY).days
+        christmas_end = (winter_break_day_end - Parameters.OUTBREAK_FIRST_DAY).days
 
         count = 0
 
@@ -151,17 +157,33 @@ class Dependency:
         other = np.mean(self.raw_mobility.T[0:2], axis=0).T
         school = np.zeros(shape=(3000, ))
 
-        while count * 365 + no_school_start < 3000:
+        while count * 365 + summer_break_start < 3000:
             count += 1
-            start = count * 365 + no_school_start
-            end = count * 365 + no_school_end
+            start = count * 365 + summer_break_start
+            end = min(count * 365 + summer_break_end, 3000)
+            # print(start, end)
             school[start:end] = -0.8
             pass
+
+        count = 0
+
+        while count * 365 + christmas_start < 3000:
+            count += 1
+            start = count * 365 + christmas_start
+            end = min(count * 365 + christmas_end, 3000)
+            # print(start, end)
+            school[start:end] = -0.8
+            pass
+
[…]

### 2022-12-26 Model/Parameters.py

@@ -17,19 +17,19 @@ ver = '1.0'
 
 
 def get_immunity_kernel(dose=0, length=2000):
-    if dose == 0:
-        # TODO: natural immunity this is incorrect, update!
-        return np.ones(shape=TWO_DOSE_EFFICACY.shape) - 0.15 * \
-            (np.ones(shape=TWO_DOSE_EFFICACY.shape)  - TWO_DOSE_EFFICACY)
-    elif dose == 1:
-        return 0.8 * TWO_DOSE_EFFICACY
-    elif dose == 2:
-        return TWO_DOSE_EFFICACY
-    elif dose == 3:
-        return THREE_DOSE_EFFICACY
-    else:
-        return np.ones(shape=(2000, 16))
-    return
+    # if dose == 0:
+    #     # TODO: natural immunity this is incorrect, update!
+    #     return np.ones(shape=TWO_DOSE_EFFICACY.shape) - 0.15 * \
+    #         (np.ones(shape=TWO_DOSE_EFFICACY.shape)  - TWO_DOSE_EFFICACY)
+    # elif dose == 1:
+    #     return 0.8 * TWO_DOSE_EFFICACY
+    # elif dose == 2:
+    #     return TWO_DOSE_EFFICACY
+    # elif dose == 3:
+    #     return THREE_DOSE_EFFICACY
+    # else:
+    #     return np.ones(shape=(2000, 16))
+    return np.ones(shape=(2000, 16))
 
 
 DEPENDENCY_PATH = os.getcwd()[:-5] + 'Model Dependencies/'

### 2022-12-26 R code/Vaccine_paper.R

@@ -1,0 +1,30 @@
+library('ggplot2')
+
+
+df <- read.csv('D:/Github/Commuting_TSF_SARS-Cov-2_model_master/Analysis/Probabilistic_analysis/Raw_for_analysis/vaccine_paper_2.csv')
+
+p <- ggplot(df) + ylab('Effectiveness') + xlab('Months since vaccination') +
+  geom_point(aes(x = Month, y = Effectiveness, color=Source)) + 
+  geom_line(aes(x = Month, y = Effectiveness, color=Source)) +
+  geom_ribbon(aes(x = Month, ymin = Effectiveness_min, ymax = Effectiveness_max, fill=Source), alpha=0.5) +
+  facet_grid(Type ~ Dose) 
+
+p
+
+write.csv(df, 'back_up.csv')
+
+ggsave("two_papers.jpg", width = 15, height = 6)
+
+p <- ggplot(df) + ylab('Frequency') + xlab('Months upon immumnity gain') +
+  geom_point(aes(x = Month, y = Recovered_vaccinated, color='blue')) + 
+  geom_line(aes(x = Month, y = Recovered_vaccinated, color='blue')) +
+  geom_point(aes(x = Month, y = Vaccined_recovered, color='green')) + 
+  geom_line(aes(x = Month, y = Vaccined_recovered, color='green')) +
+  geom_point(aes(x = Month, y = Two_dose, color='red')) +
+  geom_line(aes(x = Month, y = Two_dose, color='red')) +
+  scale_colour_discrete(name = "Cohort", labels = c("Hybird immunity 1", "Hybird immunity 2", "Vaccine immunity (2 dose)")) + 
+  facet_grid(. ~ Age_band) 
+
+p
+
+ggsave("vaccine_vaccined.jpg", width = 10, height = 3)

### 2022-12-26 Model/Dependency.py
Trend fits, but need to revise vaccination data.

@@ -2,6 +2,7 @@ import copy
 from datetime import datetime
 
 import cv2
+import matplotlib.pyplot as plt
 import numpy as np
 import os
 import csv
@@ -11,6 +12,7 @@ import pandas as pd
 import Gaussian
 import Parameters
 import Util
+
 
 class Dependency:
     county_data = np.zeros((Parameters.NO_COUNTY, 3), dtype=int)
@@ -97,7 +99,6 @@ class Dependency:
         self.read_mobility()
         self.mobility_reshape()
 
-
     def read_mobility(self):
         path = self.get_dependency_path()
         read_path = path + 'Region_Mobility_Report_CSVs/'
@@ -135,7 +136,6 @@ class Dependency:
         self.raw_mobility = mobility.T
         return
 
-
     def mobility_reshape(self):
         year_forecast = 10
         summer_break_day_start = datetime.strptime('2020-04-25', '%Y-%m-%d')
@@ -155,14 +155,14 @@ class Dependency:
         work = np.mean(self.raw_mobility.T[3:5], axis=0).T
         residential = self.raw_mobility.T[5]
         other = np.mean(self.raw_mobility.T[0:2], axis=0).T
-        school = np.zeros(shape=(3000, ))
+        school = np.zeros(shape=(3000,))
 
         while count * 365 + summer_break_start < 3000:
             count += 1
             start = count * 365 + summer_break_start
             end = min(count * 365 + summer_break_end, 3000)
             # print(start, end)
-            school[start:end] = -0.8
+            school[start:end] = - 0.65
             pass
 
         count = 0
@@ -172,11 +172,11 @@ class Dependency:
             start = count * 365 + christmas_start
             end = min(count * 365 + christmas_end, 3000)
             # print(start, end)
-            school[start:end] = -0.8
+            school[start:end] = - 0.65
             pass
 
-        school = np.reshape(cv2.GaussianBlur(school.reshape(3000, 1), (7, 7), 0), newshape=(3000,))
-
+        school = np.reshape(cv2.GaussianBlur(school.reshape(3000, 1), (7, 7), 0), newshape=(3000,)) \
+                 - 0.2 * np.ones(shape=school.shape)
 
         conct = np.concatenate([residential.reshape(3000, 1), school.reshape(3000, 1),
                                 work.reshape(3000, 1), other.reshape(3000, 1)], axis=1)
[…]

### 2022-12-26 Model/Model.py

@@ -79,7 +79,8 @@ class Model:
 
         today_population = np.ones(shape=(population.shape[0], population.shape[1])) * population
 
-        today_cases = self._model_data.time_series_infected.transpose(1, 0, 2)[:date]
+        today_cases = self._model_data.time_series_active_cases.transpose(1, 0, 2)[:date]
+        # today_cases = self._model_data.time_series_infected.transpose(1, 0, 2)[:date]
 
         today_incidence = today_cases
 
@@ -164,10 +165,17 @@ class Model:
     def _susceptible_to_exposed(self, date, time_step='day'):
         for c in range(Parameters.NO_COUNTY):
             immunity_level = self._model_data.time_series_immunity[c][date - 1]
+
             immunity = np.ones(shape=(16,)) - immunity_level
 
-            clinical_infectious = np.sum(self._model_data.time_series_clinical_cases[c][date - 5:date], axis=0)
-            sub_clinical_infectious = np.sum(self._model_data.time_series_clinical_cases[c][date - 3:date], axis=0)
+            if c == 0:
+                print('Coefficient', immunity)
+                print('RAW_IMMUNITY', immunity_level)
+                print('Mobility', self.dependency.mobility[self.date])
+
+            clinical_infectious = np.sum(self._model_data.time_series_clinical_cases[c][date - 2:date], axis=0)
+            # sub_clinical_infectious = np.sum(self._model_data.time_series_clinical_cases[c][date - 3:date], axis=0) ?
+            sub_clinical_infectious = np.sum(self._model_data.time_series_clinical_cases[c][date - 2:date], axis=0)
             exposed_infectious = np.sum(self._model_data.time_series_exposed[c][date - 3:date], axis=0)
 
             tot_infectiouesness = clinical_infectious + 0.5 * (sub_clinical_infectious + exposed_infectious)
@@ -178,7 +186,6 @@ class Model:
                 type = 0
             else:
                 type = 1
-
 
             rslt = self._get_new_cases(tot_infectiouesness, contact_type=type, contact_pattern=time_step) * immunity
             # print(rslt)

### 2022-12-26 Model/Parameters.py

@@ -16,27 +16,36 @@ import datetime
 ver = '1.0'
 
 
+def log_fit(x, a=0, b=0, c=0):
+    return a * np.exp(-b * x) + c
+
 def get_immunity_kernel(dose=0, length=2000):
-    # if dose == 0:
-    #     # TODO: natural immunity this is incorrect, update!
-    #     return np.ones(shape=TWO_DOSE_EFFICACY.shape) - 0.15 * \
-    #         (np.ones(shape=TWO_DOSE_EFFICACY.shape)  - TWO_DOSE_EFFICACY)
-    # elif dose == 1:
-    #     return 0.8 * TWO_DOSE_EFFICACY
-    # elif dose == 2:
-    #     return TWO_DOSE_EFFICACY
-    # elif dose == 3:
-    #     return THREE_DOSE_EFFICACY
-    # else:
-    #     return np.ones(shape=(2000, 16))
+    if dose == 0:
+        return INFECTION_IMMUNITY
+    elif dose == 1:
+        return 0.8 * TWO_DOSE_EFFICACY
+    elif dose == 2:
+        return TWO_DOSE_EFFICACY
+    elif dose == 3:
+        return THREE_DOSE_EFFICACY
+    else:
+        return np.ones(shape=(2000, 16))
     return np.ones(shape=(2000, 16))
 
 
 DEPENDENCY_PATH = os.getcwd()[:-5] + 'Model Dependencies/'
 
-TWO_DOSE_EFFICACY = df = pd.read_csv(DEPENDENCY_PATH + 'two_dose.csv', delimiter=',').to_numpy().T[1:17].T
-THREE_DOSE_EFFICACY = df = pd.read_csv(DEPENDENCY_PATH + 'three_dose.csv', delimiter=',').to_numpy().T[1:17].T
+# TWO_DOSE_EFFICACY = pd.read_csv(DEPENDENCY_PATH + 'two_dose.csv', delimiter=',').to_numpy().T[1:17].T
+# THREE_DOSE_EFFICACY = pd.read_csv(DEPENDENCY_PATH + 'three_dose.csv', delimiter=',').to_numpy().T[1:17].T
 
+TWO_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=62.715, b=0.004, c=10).reshape(2000, 1),
+                                np.ones(shape=(16, 1)).T) / 100
+
[…]

### 2022-12-26 R code/Vaccine_non_age_specific_efficacy.R

@@ -1,0 +1,18 @@
+library('ggplot2')
+library("ggsci")
+
+df <- read.csv('D:/Github/Commuting_TSF_SARS-Cov-2_model_master/Analysis/Probabilistic_analysis/Infereced_data/Vaccine_effectiveness.csv')
+
+# colnames(df) <- c('Dose', 'Days', 'mean', 'mean_min', 'mean_max', 'predicted', 'Andrews_et_al', 'Andrews_et_al_max', 'Andrews_et_al_min', 'Ferdinands_et_al', 'Ferdinands_et_al_max', 'Ferdinands_et_al_min', 'CDC', 'CDC_max', 'CDC_min')
+
+colnames(df) <- c('Dose','Source', 'Days', 'mean', 'mean_min', 'mean_max', 'predicted')
+
+p <- ggplot(df) + ylab('Effectiveness') + xlab('Days since vaccination') +
+  geom_ribbon(aes(x = Days, ymin=mean_max, ymax=mean_min, fill=Source), alpha=0.3) +
+  geom_line(aes(x = Days, y = mean, color=Source), size=0.75) +
+  geom_line(aes(x = Days, y = predicted), size=0.75, color='black', linetype=2) +
+  scale_color_nejm() + scale_fill_nejm() +
+  facet_grid(. ~ Dose) 
+
+p
+

### 2022-12-26 R code/Vaccine_paper.R

@@ -3,7 +3,7 @@ library('ggplot2')
 
 df <- read.csv('D:/Github/Commuting_TSF_SARS-Cov-2_model_master/Analysis/Probabilistic_analysis/Raw_for_analysis/vaccine_paper_2.csv')
 
-p <- ggplot(df) + ylab('Effectiveness') + xlab('Months since vaccination') +
+p <- ggplot(df) + ylab('Effectiveness') + xlab('Weeks since vaccination') +
   geom_point(aes(x = Month, y = Effectiveness, color=Source)) + 
   geom_line(aes(x = Month, y = Effectiveness, color=Source)) +
   geom_ribbon(aes(x = Month, ymin = Effectiveness_min, ymax = Effectiveness_max, fill=Source), alpha=0.5) +
@@ -11,7 +11,7 @@ p <- ggplot(df) + ylab('Effectiveness') + xlab('Months since vaccination') +
 
 p
 
-write.csv(df, 'back_up.csv')
+ write.csv(df, 'back_up.csv')
 
 ggsave("two_papers.jpg", width = 15, height = 6)
 

### 2022-12-26 Model/Dependency.py
Tuning the model, bug fixes.

@@ -44,6 +44,8 @@ class Dependency:
     date_to_hospitalization_rate_by_phu = dict()
     date_to_death_rate_by_phu = dict()
     date_to_vaccines_by_age = np.zeros((0, 3, 9))
+    date_to_vaccines_by_age_un_reshaped = np.zeros((0, 3, 9))
+    date_to_vaccines_by_age_un_differentaited = np.zeros((0, 3, 9))
 
     """
         County-specific data
@@ -358,6 +360,11 @@ class Dependency:
         """
 
         # global date_to_vaccines_by_age
+
+        self.date_to_vaccines_by_age_un_reshaped = copy.deepcopy(self.date_to_vaccines_by_age)
+
+        # print(self.date_to_vaccines_by_county.shape)
+
         reshaped = np.zeros((self.total_days, 3, 16))
 
         for date in range(self.total_days):
@@ -367,6 +374,8 @@ class Dependency:
                 reshaped[date][dose] = lst
 
         self.date_to_vaccines_by_age = reshaped
+
+        self.date_to_vaccines_by_age_un_differentaited = copy.deepcopy(self.date_to_vaccines_by_age )
 
         return
 
@@ -381,7 +390,11 @@ class Dependency:
         data = self.date_to_vaccines_by_age.transpose(1, 0, 2)
         dose1 = np.clip((data[0] - data[1]), a_min=0, a_max=1)
         dose2 = np.clip((data[1] - data[2]), a_min=0, a_max=1)
-        dose3 = (data[2])
+
+        # dose1 = data[0]
+        # dose2 = data[1]
+        dose3 = data[2]
+
         self.date_to_vaccines_by_age = np.array([dose1, dose2, dose3]).transpose(1, 0, 2)
 
         for i in range(self.total_days - 1):
@@ -519,4 +532,11 @@ class Dependency:
 
 if __name__ == '__main__':
     dependency = Dependency()
+    reshaped_data = dependency.date_to_vaccines_by_age_un_differentaited.transpose(1, 0, 2)[0]
+    data = dependency.date_to_vaccines_by_age_un_reshaped.transpose(1, 0, 2)[0]
+    print()
+    plt.plot(data)
+    plt.show()
+    plt.plot(reshaped_data)
+    plt.show()
     pass

### 2022-12-26 Model/Gaussian.py

@@ -1,4 +1,7 @@
 import math
+
+import matplotlib.pyplot as plt
+
 import Parameters
 import numpy as np
 import cv2
@@ -10,6 +13,7 @@ def blur(lst):
         :return:
     """
     raw = np.zeros(shape=(100, ))
+    print(lst)
     raw[5:12] = lst[0]
     raw[12:18] = lst[1]
     raw[18:30] = lst[2]
@@ -20,15 +24,17 @@ def blur(lst):
     raw[70:80] = lst[7]
     raw[80:] = lst[8]
 
+    # raw = raw * Parameters.RAW_AGE_DISTRIBUTION / Parameters.ONT_POPULATOIN
+
     blurred = np.reshape(np.array(cv2.GaussianBlur(raw.reshape(100, 1), (9, 9), 0)), newshape=(100,))
+
 
     rslt = np.zeros(shape=(16, ))
 
     for i in range(15):
-        rslt[i] = np.sum(blurred[5 * i:5 * i + 5]) * Parameters.ONT_AGE_BAND_POPULATION[i]
-    rslt[15] = np.sum(blurred[75:]) * Parameters.ONT_AGE_BAND_POPULATION[15]
-
-    return rslt / Parameters.ONT_POPULATOIN
+        rslt[i] = np.sum(blurred[5 * i:5 * i + 5]) / 5
+    rslt[15] = np.sum(blurred[75:]) / 25
+    return rslt
 
 
 def age_dog_algo(lst):
@@ -36,3 +42,9 @@ def age_dog_algo(lst):
         return np.zeros(shape=(16, ))
     else:
         return blur(lst)
+
+if __name__ == '__main__':
+    test = np.ones(shape=(9, ))
+    rslt = age_dog_algo(test)
+    plt.plot(rslt)
+    plt.show()

### 2022-12-26 Model/Model.py

@@ -109,7 +109,7 @@ class Model:
         infection_immunized = np.sum(np.multiply(today_incidence, kernel_infection), axis=0)
 
         # vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose1_rmv - immunity_dose2_rmv
-        vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose2_rmv
+        vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3
 
         infection_immunity = infection_immunized / today_population
         vaccine_immunized = vaccine_immunity * today_population

### 2022-12-26 Model/Parameters.py

@@ -12,6 +12,7 @@ from Util import normalize
 import matplotlib.pyplot as plt
 import numpy as np
 import datetime
+import cv2
 
 ver = '1.0'
 
@@ -131,7 +132,7 @@ SUSC_RATIO = np.array([3.991327254652800027e-01, 3.948075309394725174e-01, 4.022
 
 CLINICAL_RATIO = np.array([0.2865309, 0.26753682, 0.23495708, 0.23019938, 0.25561971, 0.28454104,
                            0.31587461, 0.34737841, 0.38386853, 0.42265894, 0.47025061, 0.52584302,
-                           0.59291004, 0.64122657, 0.67295434, 0.71677774]) * 1
+                           0.59291004, 0.64122657, 0.67295434, 0.71677774])
 
 SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - CLINICAL_RATIO
 
@@ -159,6 +160,16 @@ AGE_BANDS = ['0-4yrs', '5-9yrs', '10-14yrs', '15-19yrs', '20-24yrs', '25-29yrs',
 """
     Convolutional kernels
 """
+
+raw_age_df = pd.read_csv(os.getcwd()[:-5] + 'Model Dependencies/' + '1710000501-eng.csv')
+raw_age_dist = raw_age_df['Persons'].to_numpy()[1:].reshape(21, 1) * np.ones(shape=(1, 5))
+raw_age_dist = raw_age_dist.flatten() / 5
+raw_age_dist = np.reshape(np.array(cv2.GaussianBlur(raw_age_dist.reshape(105, 1), (9, 9), 0)),
+                                      newshape=(105,))
+
+RAW_AGE_DISTRIBUTION = np.zeros(shape=(100, ))
+RAW_AGE_DISTRIBUTION[:100] = raw_age_dist[:100]
+RAW_AGE_DISTRIBUTION[99] = np.sum(raw_age_dist[100:])
 
 EXP2ACT_RATIO = np.ones(shape=(16,))
 

### 2022-12-26 Model/Parameters.py
update

@@ -45,8 +45,11 @@ TWO_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=62.715, b=
 THREE_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=93.327, b=0.003, c=0).reshape(2000, 1),
                                 np.ones(shape=(16, 1)).T) / 100
 
-INFECTION_IMMUNITY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=100, b=0.002, c=0).reshape(2000, 1),
-                                np.ones(shape=(16, 1)).T) / 100
+# INFECTION_IMMUNITY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=100, b=0.002, c=0).reshape(2000, 1),
+#                                 np.ones(shape=(16, 1)).T) / 100
+
+INFECTION_IMMUNITY = np.ones(shape=TWO_DOSE_EFFICACY.shape) - \
+                     (np.ones(shape=TWO_DOSE_EFFICACY.shape) - TWO_DOSE_EFFICACY) * 0.154
 INFECTIOUSNESS = 0.08
 
 """

### 2022-12-27 Model/Dependency.py
Update model.

@@ -164,7 +164,7 @@ class Dependency:
             start = count * 365 + summer_break_start
             end = min(count * 365 + summer_break_end, 3000)
             # print(start, end)
-            school[start:end] = - 0.65
+            school[start:end] = - 0.75
             pass
 
         count = 0
@@ -174,7 +174,7 @@ class Dependency:
             start = count * 365 + christmas_start
             end = min(count * 365 + christmas_end, 3000)
             # print(start, end)
-            school[start:end] = - 0.65
+            school[start:end] = - 0.75
             pass
 
         school = np.reshape(cv2.GaussianBlur(school.reshape(3000, 1), (7, 7), 0), newshape=(3000,)) \

### 2022-12-27 Model/Model.py

@@ -91,11 +91,17 @@ class Model:
         raw_kernel_dose_3 = (Parameters.VACCINE_EFFICACY_KERNEL_DOSE3[:date])[::-1]
         raw_kernel_infection = (Parameters.INFECTION_EFFICACY_KERNEL[:date])[::-1]
 
+        raw_kernel_dose_1_rmv = (Parameters.ONE_DOSE_EFFICACY_RMV[:date])[::-1]
+        raw_kernel_dose_2_rmv = (Parameters.TWO_DOSE_EFFICACY_RMV[:date])[::-1]
+
         ratio = np.ones(shape=(1, Parameters.NO_COUNTY, 1))
         kernel_dose_1 = np.multiply(raw_kernel_dose_1.reshape(date, 1, 16), ratio)
         kernel_dose_2 = np.multiply(raw_kernel_dose_2.reshape(date, 1, 16), ratio)
         kernel_dose_3 = np.multiply(raw_kernel_dose_3.reshape(date, 1, 16), ratio)
         kernel_infection = np.multiply(raw_kernel_infection.reshape(date, 1, 16), ratio)
+
+        kernel_remove_dose_1 = np.multiply(raw_kernel_dose_1_rmv.reshape(date, 1, 16), ratio)
+        kernel_remove_dose_2 = np.multiply(raw_kernel_dose_2_rmv.reshape(date, 1, 16), ratio)
 
         raw_sum = np.sum(today_incidence, axis=0)
 
@@ -103,13 +109,13 @@ class Model:
         immunity_dose2 = np.sum(np.multiply(dose2, kernel_dose_2), axis=0)
         immunity_dose3 = np.sum(np.multiply(dose3, kernel_dose_3), axis=0)
 
-        immunity_dose1_rmv = np.sum(np.multiply(dose2, kernel_dose_1), axis=0)
-        immunity_dose2_rmv = np.sum(np.multiply(dose3, kernel_dose_2), axis=0)
+        immunity_dose1_rmv = np.sum(np.multiply(dose2, kernel_remove_dose_1), axis=0)
+        immunity_dose2_rmv = np.sum(np.multiply(dose3, kernel_remove_dose_2), axis=0)
 
         infection_immunized = np.sum(np.multiply(today_incidence, kernel_infection), axis=0)
 
-        # vaccine_immunity = immunity_dose1 + immunity_dose2 + immunity_dose3 - immunity_dose1_rmv - immunity_dose2_rmv
[…]

### 2022-12-27 Model/Parameters.py

@@ -39,17 +39,23 @@ DEPENDENCY_PATH = os.getcwd()[:-5] + 'Model Dependencies/'
 # TWO_DOSE_EFFICACY = pd.read_csv(DEPENDENCY_PATH + 'two_dose.csv', delimiter=',').to_numpy().T[1:17].T
 # THREE_DOSE_EFFICACY = pd.read_csv(DEPENDENCY_PATH + 'three_dose.csv', delimiter=',').to_numpy().T[1:17].T
 
-TWO_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=62.715, b=0.004, c=10).reshape(2000, 1),
+TWO_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=60.241, b=0.004, c=13.873).reshape(2000, 1),
                                 np.ones(shape=(16, 1)).T) / 100
 
-THREE_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=93.327, b=0.003, c=0).reshape(2000, 1),
+THREE_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=73.576, b=0.005, c=20).reshape(2000, 1),
                                 np.ones(shape=(16, 1)).T) / 100
 
-# INFECTION_IMMUNITY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=100, b=0.002, c=0).reshape(2000, 1),
-#                                 np.ones(shape=(16, 1)).T) / 100
+ONE_DOSE_EFFICACY_RMV = np.concatenate([0.8 * TWO_DOSE_EFFICACY[60:],
+                                        np.zeros(shape=(60, 16))], axis=0)
 
-INFECTION_IMMUNITY = np.ones(shape=TWO_DOSE_EFFICACY.shape) - \
-                     (np.ones(shape=TWO_DOSE_EFFICACY.shape) - TWO_DOSE_EFFICACY) * 0.154
+TWO_DOSE_EFFICACY_RMV = np.concatenate([TWO_DOSE_EFFICACY[60:],
+                                        np.zeros(shape=(60, 16))], axis=0)
+
+
[…]

### 2022-12-28 Manuscripts/main.tex
too lazy to write
Update new files.
Tuning the model, bug fixes.
Update

@@
 \usepackage{color}
+\usepackage{svg}
 \usepackage{xcolor}
@@
 
-\mainfigure Essentially, the model takes in
-\begin{enumerate}
-    \item \important{PAST} Time-series data of the no. cases in Ontario in 26 PHUs
-    \item \important{PAST} Time-series data of the ratio of 1st, 2nd, and 3rd dose vaccination in Ontario
-    \item Labour force data and the commute matrix in Ontario
-    \item Contact Matrix and CoMix
-    \item \important{PREDICTED} Google mobility data in Ontario \emphasize{(Generated from NN)}
-    \item Epidemiological parameters
-    \item Vaccine parameters and time-series data of the \important{PREDICTED} immunity waning effects
-    \item Whether we use machine learning to address the
-\end{enumerate}
-and outputs
-\begin{itemize}
-    \item no. cases in each district
-    \item no. severe cases (ICU occupancy) in each district
-    \item no. deaths in each district
-\end{itemize}
+\newpage
+
+\section{Supplementary analysis}
+
+\begin{figure}[h]
+    \includegraphics*[width=\textwidth]{vaccine_unvaccinated.jpg}
+    \includegraphics*[width=\textwidth]{vaccine_vaccined.jpg}
+    \textbf{Figure S1:} Relative effectiveness of natural, vaccine, and hybrid immunity.
+\end{figure}
+
+\begin{figure}[h]
+    \includegraphics*[width=\textwidth]{Three_paper_avg.jpg}
+    \textbf{Figure S1:} Estimating the effectiveness of 2 and 3 doses of vaccination against clinical infection of the omicron variant of SARS-Cov-2.
+\end{figure}
+
+\newpage
 
@@
     \begin{table}[h]
-    \caption{Convolutional kernels in the model as probability distributions}
+    \caption{Epidemiological convolutional kernels in the model as probability distributions}
     \centering

### 2022-12-28 Model/Dependency.py

@@ -154,9 +154,9 @@ class Dependency:
 
         count = 0
 
-        work = np.mean(self.raw_mobility.T[3:5], axis=0).T
-        residential = self.raw_mobility.T[5]
-        other = np.mean(self.raw_mobility.T[0:2], axis=0).T
+        work = self.raw_mobility.T[3]
+        residential = self.raw_mobility.T[4]
+        other = (self.raw_mobility.T[0] * 0.345 + self.raw_mobility.T[1] * 0.21 + self.raw_mobility.T[3] * 0.445).T
         school = np.zeros(shape=(3000,))
 
         while count * 365 + summer_break_start < 3000:

### 2022-12-28 Model/Model.py

@@ -324,6 +324,7 @@ class Model:
             # print(Parameters.MATRIX_CONTACT_TYPE[j], self.dependency.mobility[self.date][j])
             matrix = np.add(matrix, preset[j] * matrices[contact_type][j] * self.dependency.mobility[self.date][j])
         # return matrix * self.infectiousness
+        matrix = matrix * Parameters.SEASONALITY[self.date]
         return matrix.T * self.infectiousness
 
     def _initialize_dependencies(self):

### 2022-12-28 Model/Parameters.py

@@ -33,6 +33,13 @@ def get_immunity_kernel(dose=0, length=2000):
         return np.ones(shape=(2000, 16))
     return np.ones(shape=(2000, 16))
 
+def get_seasonality(factor=0.2, length=2000):
+    raw = np.linspace(0, 2499, length+500)
+    shift = (OUTBREAK_FIRST_DAY - datetime.datetime(2020, 1, 1)).days
+    raw = raw * 2 * math.pi / 360
+    kernel = np.cos(raw)[shift:shift + length]
+    rslt = kernel * factor + np.ones(shape=kernel.shape)
+    return rslt
 
 DEPENDENCY_PATH = os.getcwd()[:-5] + 'Model Dependencies/'
 
@@ -71,6 +78,7 @@ NIGHT_PRESET = np.ones(shape=(4, )) - DAY_PRESET
 MATRIX_PRESETS = {'day': DAY_PRESET,
                   'night': NIGHT_PRESET
                   }
+
 
 # MATRIX_PRESETS = {'day': np.array([0, 1.0, 0, 0]),
 #                   'night': np.zeros(shape=(4, ))
@@ -226,6 +234,8 @@ VACCINE_EFFICACY_KERNEL_DOSE2 = get_immunity_kernel(dose=2)
 VACCINE_EFFICACY_KERNEL_DOSE3 = get_immunity_kernel(dose=3)
 
 INFECTION_EFFICACY_KERNEL = get_immunity_kernel(dose=0)
+
+SEASONALITY = get_seasonality(factor=0.1)
 
 if __name__ == '__main__':
     plt.plot(get_immunity_kernel(dose=0))

### 2022-12-28 R code/Vaccine_non_age_specific_efficacy.R

@@ -16,3 +16,5 @@ p <- ggplot(df) + ylab('Effectiveness') + xlab('Days since vaccination') +
 
 p
 
+ggsave("Three_paper_avg.jpg", width = 8, height = 4, dpi=600)
+

### 2022-12-28 Model/Parameters.py
Just fixed a major bug.

@@ -35,7 +35,7 @@ def get_immunity_kernel(dose=0, length=2000):
 
 def get_seasonality(factor=0.2, length=2000):
     raw = np.linspace(0, 2499, length+500)
-    shift = (OUTBREAK_FIRST_DAY - datetime.datetime(2020, 1, 1)).days
+    shift = 365 + (OUTBREAK_FIRST_DAY - datetime.datetime(2020, 2, 14)).days
     raw = raw * 2 * math.pi / 360
     kernel = np.cos(raw)[shift:shift + length]
     rslt = kernel * factor + np.ones(shape=kernel.shape)
@@ -156,17 +156,17 @@ SUSC_RATIO = np.array([3.991327254652800027e-01, 3.948075309394725174e-01, 4.022
 
 CLINICAL_RATIO = np.array([0.2865309, 0.26753682, 0.23495708, 0.23019938, 0.25561971, 0.28454104,
                            0.31587461, 0.34737841, 0.38386853, 0.42265894, 0.47025061, 0.52584302,
-                           0.59291004, 0.64122657, 0.67295434, 0.71677774])
+                           0.59291004, 0.64122657, 0.67295434, 0.71677774]) * 0.8
 
 SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - CLINICAL_RATIO
 
-OMICRON_CLINICAL_RATIO = CLINICAL_RATIO * 0.3
+OMICRON_CLINICAL_RATIO = CLINICAL_RATIO * 0.4
 
 REVERSE_CLINICAL_BY_AGE = np.ones(shape=CLINICAL_RATIO.shape) / CLINICAL_RATIO
 
 OMICRON_SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - OMICRON_CLINICAL_RATIO
 
-OMICRON_REVERSE_CLINICAL_BY_AGE = np.ones(shape=OMICRON_SUBCLINICAL_RATIO.shape) / OMICRON_SUBCLINICAL_RATIO
+OMICRON_REVERSE_CLINICAL_BY_AGE = np.ones(shape=OMICRON_SUBCLINICAL_RATIO.shape) / OMICRON_CLINICAL_RATIO
 
 # Work force
 LABOUR_FORCE_BY_AGE = np.array([0, 0, 0.010693183, 0.032079549, 0.083009492, 0.106146399, 0.106351741,

### 2022-12-28 Model/Dependency.py
Update markdown

@@ -164,7 +164,11 @@ class Dependency:
             start = count * 365 + summer_break_start
             end = min(count * 365 + summer_break_end, 3000)
             # print(start, end)
+<<<<<<< Updated upstream
             school[start:end] = - 0.65
+=======
+            school[start:end] = - 0.6
+>>>>>>> Stashed changes
             pass
 
         count = 0
@@ -174,11 +178,15 @@ class Dependency:
             start = count * 365 + christmas_start
             end = min(count * 365 + christmas_end, 3000)
             # print(start, end)
+<<<<<<< Updated upstream
             school[start:end] = - 0.65
+=======
+            school[start:end] = - 0.6
+>>>>>>> Stashed changes
             pass
 
         school = np.reshape(cv2.GaussianBlur(school.reshape(3000, 1), (7, 7), 0), newshape=(3000,)) \
-                 - 0.2 * np.ones(shape=school.shape)
+                 - 0.3 * np.ones(shape=school.shape)
 
         conct = np.concatenate([residential.reshape(3000, 1), school.reshape(3000, 1),
                                 work.reshape(3000, 1), other.reshape(3000, 1)], axis=1)

### 2022-12-28 Model/Model.py

@@ -31,20 +31,26 @@ class Model:
         self.model_fitting = fitting
         return
 
-    def run_one_cycle(self, display_status=False):
+    def run_one_cycle(self, display_status=False, recompute_immunity=True):
         """
         Firstly, we convert the number of newly infected cases to active cases
         """
         self.date += 1
-        self._compute_immunity(self.date)
+
+        if recompute_immunity:
+            self._compute_immunity(self.date)
+
         self._model_transition(time_step='day')
 
-        self._compute_immunity(self.date)
+        if recompute_immunity:
+            self._compute_immunity(self.date)
+
         self._model_transition(time_step='night')
 
         if display_status:
             self.print_data(self.date)
             print(self.dependency.mobility[self.date])
+
         return
 
     def print_data(self, date):
@@ -156,13 +162,15 @@ class Model:
             self._infected_to_removed(self.date)
             self._infected_to_death(self.date)
 
-    def _get_new_cases(self, cases, contact_type=0, contact_pattern='day'):
+    def _get_new_cases(self, cases, contact_type=0, contact_pattern='day', immunity=np.ones(shape=(16, ))):
         susceptibility = Parameters.SUSC_RATIO
         matrix = self._synthesize_matrix(contact_type, contact_pattern)
-        rslt = np.matmul(matrix, cases) * susceptibility
+        rslt = np.matmul(matrix, cases) * susceptibility * np.clip(immunity, a_min=0, a_max=1) * self.infectiousness
         return rslt
 
     def _susceptible_to_exposed(self, date, time_step='day'):
+
+
         for c in range(Parameters.NO_COUNTY):
             immunity_level = self._model_data.time_series_immunity[c][date - 1]
 
@@ -183,12 +191,18 @@ class Model:
             county_data = self.dependency.county_data[c]
 
             if county_data[2] > 10000:
-                type = 0
+                county_type = 0
             else:
-                type = 1
+                county_type = 1
 
+            rslt = self._get_new_cases(tot_infectiouesness, contact_type=county_type, contact_pattern=time_step,
+                                       immunity=np.clip(immunity, a_min=0, a_max=1))
+
+<<<<<<< Updated upstream
             rslt = self._get_new_cases(tot_infectiouesness, contact_type=type, contact_pattern=time_step) * immunity
             # print(rslt)
+=======
+>>>>>>> Stashed changes
             if time_step == 'day':
[…]

### 2022-12-28 Model/Parameters.py

@@ -48,8 +48,21 @@ THREE_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=93.327, 
 # INFECTION_IMMUNITY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=100, b=0.002, c=0).reshape(2000, 1),
 #                                 np.ones(shape=(16, 1)).T) / 100
 
+<<<<<<< Updated upstream
 INFECTION_IMMUNITY = np.ones(shape=TWO_DOSE_EFFICACY.shape) - \
                      (np.ones(shape=TWO_DOSE_EFFICACY.shape) - TWO_DOSE_EFFICACY) * 0.154
+=======
+TWO_DOSE_EFFICACY_RMV = np.concatenate([TWO_DOSE_EFFICACY[60:],
+                                        np.zeros(shape=(60, 16))], axis=0)
+
+INFECTION_IMMUNITY = np.ones(shape=THREE_DOSE_EFFICACY.shape) - \
+                     (np.ones(shape=THREE_DOSE_EFFICACY.shape) - THREE_DOSE_EFFICACY) * 0.5
+
+# INFECTION_IMMUNITY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=100, b=0.001, c=0).reshape(2000, 1),
+#                                 np.ones(shape=(16, 1)).T) / 100
+
+
+>>>>>>> Stashed changes
 INFECTIOUSNESS = 0.08
 
 """
@@ -141,6 +154,15 @@ SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - CLINICAL_RATIO
 
 REVERSE_CLINICAL_BY_AGE = np.ones(shape=CLINICAL_RATIO.shape) / CLINICAL_RATIO
 
+<<<<<<< Updated upstream
+=======
+OMICRON_CLINICAL_RATIO = CLINICAL_RATIO * 0.8
+
+OMICRON_SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - OMICRON_CLINICAL_RATIO
+
+OMICRON_REVERSE_CLINICAL_BY_AGE = np.ones(shape=OMICRON_SUBCLINICAL_RATIO.shape) / OMICRON_CLINICAL_RATIO
+
+>>>>>>> Stashed changes
 # Work force
[…]

### 2022-12-28 Model/Dependency.py
Update markdown

@@ -164,11 +164,7 @@ class Dependency:
             start = count * 365 + summer_break_start
             end = min(count * 365 + summer_break_end, 3000)
             # print(start, end)
-<<<<<<< Updated upstream
             school[start:end] = - 0.65
-=======
-            school[start:end] = - 0.6
->>>>>>> Stashed changes
             pass
 
         count = 0
@@ -178,11 +174,7 @@ class Dependency:
             start = count * 365 + christmas_start
             end = min(count * 365 + christmas_end, 3000)
             # print(start, end)
-<<<<<<< Updated upstream
             school[start:end] = - 0.65
-=======
-            school[start:end] = - 0.6
->>>>>>> Stashed changes
             pass
 
         school = np.reshape(cv2.GaussianBlur(school.reshape(3000, 1), (7, 7), 0), newshape=(3000,)) \

### 2022-12-28 Model/Parameters.py

@@ -48,11 +48,14 @@ THREE_DOSE_EFFICACY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=93.327, 
 # INFECTION_IMMUNITY = np.multiply(log_fit(np.linspace(0, 1999, 2000), a=100, b=0.002, c=0).reshape(2000, 1),
 #                                 np.ones(shape=(16, 1)).T) / 100
 
-<<<<<<< Updated upstream
+
 INFECTION_IMMUNITY = np.ones(shape=TWO_DOSE_EFFICACY.shape) - \
-                     (np.ones(shape=TWO_DOSE_EFFICACY.shape) - TWO_DOSE_EFFICACY) * 0.154
-=======
+                     (np.ones(shape=TWO_DOSE_EFFICACY.shape) - TWO_DOSE_EFFICACY) * 0.5
+
 TWO_DOSE_EFFICACY_RMV = np.concatenate([TWO_DOSE_EFFICACY[60:],
+                                        np.zeros(shape=(60, 16))], axis=0)
+
+TWO_DOSE_EFFICACY_RMV = np.concatenate(0.8 * [TWO_DOSE_EFFICACY[60:],
                                         np.zeros(shape=(60, 16))], axis=0)
 
 INFECTION_IMMUNITY = np.ones(shape=THREE_DOSE_EFFICACY.shape) - \
@@ -62,7 +65,6 @@ INFECTION_IMMUNITY = np.ones(shape=THREE_DOSE_EFFICACY.shape) - \
 #                                 np.ones(shape=(16, 1)).T) / 100
 
 
->>>>>>> Stashed changes
 INFECTIOUSNESS = 0.08
 
 """
@@ -154,15 +156,12 @@ SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - CLINICAL_RATIO
 
 REVERSE_CLINICAL_BY_AGE = np.ones(shape=CLINICAL_RATIO.shape) / CLINICAL_RATIO
 
-<<<<<<< Updated upstream
-=======
 OMICRON_CLINICAL_RATIO = CLINICAL_RATIO * 0.8
 
 OMICRON_SUBCLINICAL_RATIO = np.ones(shape=(16,), dtype=float) - OMICRON_CLINICAL_RATIO
 
 OMICRON_REVERSE_CLINICAL_BY_AGE = np.ones(shape=OMICRON_SUBCLINICAL_RATIO.shape) / OMICRON_CLINICAL_RATIO
 
[…]

### 2022-12-28 Model/Model.py
update

@@ -97,25 +97,30 @@ class Model:
         raw_kernel_dose_3 = (Parameters.VACCINE_EFFICACY_KERNEL_DOSE3[:date])[::-1]
         raw_kernel_infection = (Parameters.INFECTION_EFFICACY_KERNEL[:date])[::-1]
 
+        raw_kernel_dose_rmv_1 = (Parameters.ONE_DOSE_EFFICACY_RMV[:date])[::-1]
+        raw_kernel_dose_rmv_2 = (Parameters.TWO_DOSE_EFFICACY_RMV[:date])[::-1]
+
         ratio = np.ones(shape=(1, Parameters.NO_COUNTY, 1))
         kernel_dose_1 = np.multiply(raw_kernel_dose_1.reshape(date, 1, 16), ratio)
         kernel_dose_2 = np.multiply(raw_kernel_dose_2.reshape(date, 1, 16), ratio)
         kernel_dose_3 = np.multiply(raw_kernel_dose_3.reshape(date, 1, 16), ratio)
         kernel_infection = np.multiply(raw_kernel_infection.reshape(date, 1, 16), ratio)
 
-        raw_sum = np.sum(today_incidence, axis=0)
+        kernel_dose_rmv_1 = np.multiply(raw_kernel_dose_rmv_1.reshape(date, 1, 16), ratio)
+        kernel_dose_rmv_2 = np.multiply(raw_kernel_dose_rmv_2.reshape(date, 1, 16), ratio)
+
 
         immunity_dose1 = np.sum(np.multiply(dose1, kernel_dose_1), axis=0)
         immunity_dose2 = np.sum(np.multiply(dose2, kernel_dose_2), axis=0)
         immunity_dose3 = np.sum(np.multiply(dose3, kernel_dose_3), axis=0)
 
-        immunity_dose1_rmv = np.sum(np.multiply(dose2, kernel_dose_1), axis=0)
-        immunity_dose2_rmv = np.sum(np.multiply(dose3, kernel_dose_2), axis=0)
+        immunity_dose1_rmv = np.sum(np.multiply(dose2, kernel_dose_rmv_1), axis=0)
+        immunity_dose2_rmv = np.sum(np.multiply(dose3, kernel_dose_rmv_2), axis=0)
 
         infection_immunized = np.sum(np.multiply(today_incidence, kernel_infection), axis=0)
 
[…]

### 2022-12-28 Model/Parameters.py

@@ -16,6 +16,13 @@ import cv2
 
 ver = '1.0'
 
+def get_seasonality(factor=0.1, length=2000):
+    raw = np.linspace(0, 2499, 2500)
+    shift = 365 + (OUTBREAK_FIRST_DAY - datetime.datetime(2020, 2, 14)).days
+    raw = raw * 2 * math.pi / 360
+    kernel = np.cos(raw)[shift:shift+2000]
+    rslt = kernel * factor + np.ones(shape=kernel.shape)
+    return rslt
 
 def log_fit(x, a=0, b=0, c=0):
     return a * np.exp(-b * x) + c
@@ -55,7 +62,7 @@ INFECTION_IMMUNITY = np.ones(shape=TWO_DOSE_EFFICACY.shape) - \
 TWO_DOSE_EFFICACY_RMV = np.concatenate([TWO_DOSE_EFFICACY[60:],
                                         np.zeros(shape=(60, 16))], axis=0)
 
-TWO_DOSE_EFFICACY_RMV = np.concatenate(0.8 * [TWO_DOSE_EFFICACY[60:],
+ONE_DOSE_EFFICACY_RMV = np.concatenate([0.8 * TWO_DOSE_EFFICACY[60:],
                                         np.zeros(shape=(60, 16))], axis=0)
 
 INFECTION_IMMUNITY = np.ones(shape=THREE_DOSE_EFFICACY.shape) - \
@@ -178,10 +185,6 @@ AGE_BANDS = ['0-4yrs', '5-9yrs', '10-14yrs', '15-19yrs', '20-24yrs', '25-29yrs',
              '45-49yrs', '50-54yrs', '55-59yrs', '60-64yrs', '65-69yrs', '70-74yrs', '75+yrs']
 
 """
-    Convolution kernels
-"""
-
-"""
     Convolutional kernels
 """
 
@@ -228,6 +231,8 @@ VACCINE_EFFICACY_KERNEL_DOSE2 = get_immunity_kernel(dose=2)
 VACCINE_EFFICACY_KERNEL_DOSE3 = get_immunity_kernel(dose=3)
 
 INFECTION_EFFICACY_KERNEL = get_immunity_kernel(dose=0)
+
+SEASONALITY = get_seasonality(factor=0.1)
 
 if __name__ == '__main__':
     plt.plot(get_immunity_kernel(dose=0))

### 2022-12-29 Model/Dependency.py
Update exposed.

@@ -182,6 +182,13 @@ class Dependency:
 
         conct = np.concatenate([residential.reshape(3000, 1), school.reshape(3000, 1),
                                 work.reshape(3000, 1), other.reshape(3000, 1)], axis=1)
+
+
+        mask_lift_date = (datetime.strptime('2020-07-01', '%Y-%m-%d') - Parameters.OUTBREAK_FIRST_DAY).days
+
+        unmodified = conct.T
+        unmodified[1][:mask_lift_date] = school[:mask_lift_date] * 0.6
+
         self.mobility = conct + np.ones(shape=conct.shape)
 
         # print(np.max(self.mobility), np.min(self.mobility))

### 2022-12-29 Model/ModelData.py

@@ -83,6 +83,8 @@ class ModelData:
 
         # TODO: split it, to delta and omicron
 
+       #  omicron_dominance_date =
+
         non_omicron = (self.time_series_clinical_cases.transpose(1, 0, 2)[:700] *
                        Parameters.REVERSE_CLINICAL_BY_AGE.T).transpose(1, 0, 2)
 
@@ -94,7 +96,13 @@ class ModelData:
         # self.time_series_active_cases = np.multiply(self.time_series_clinical_cases,
         #                                             Parameters.REVERSE_CLINICAL_BY_AGE.T)
 
-        self.time_series_exposed = copy.deepcopy(self.time_series_active_cases)
+        self.time_series_exposed = np.zeros(shape=self.time_series_active_cases.shape).transpose(1, 0, 2)
+
+        shifted = np.concatenate([self.time_series_active_cases.transpose(1, 0, 2)[3:],
+                                  self.time_series_active_cases.transpose(1, 0, 2)[-1] *
+                                  np.ones(shape=(3, 1, 1))]).transpose(1, 0, 2)
+
+        self.time_series_exposed = shifted
 
         self.time_series_infected = copy.deepcopy(self.time_series_active_cases)
 
